### 2021-01-19 article/tex/submission.tex
:fire: genesis

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

\graphicspath{{../figures}} %goes to path: figures/

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{air4children: Artificial Intelligence and Robotics for Children}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

%\author{Ben Trovato}
%\authornote{Both authors contributed equally to this research.}
%\email{trovato@corporation.com}
%\orcid{1234-5678-9012}
%\author{G.K.M. Tobin}

\author{Miguel Xochicale}
\affiliation{%
  \institution{King's College London}
  \city{London}
  \country{UK}}
\authornotemark[1]
\email{miguel.xochicale@kcl.ac.uk}

\author{John Smith}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{jsmith@affiliation.org}

\author{Julius P. Kumquat}
\affiliation{%
  \institution{The Kumquat Consortium}
  \city{New York}
  \country{USA}}
\email{jpkumquat@consortium.net}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{sampleteaser}
  \caption{Seattle Mariners at Spring Training, 2010.}
  \Description{Enjoying the baseball game from the third-base
  seats. Ichiro Suzuki preparing to bat.}
  \label{fig:teaser}
\end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|acmart|'' document class is
the {\itshape template style} which corresponds to the kind of publication
or SIG publishing the work. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals
use the {\verb|acmsmall|} template style:
\begin{itemize}
\item {\verb|acmsmall|}: The default journal template style.
\item {\verb|acmlarge|}: Used by JOCCH and TAP.
\item {\verb|acmtog|}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
\begin{itemize}
\item {\verb|acmconf|}: The default proceedings template style.
\item{\verb|sigchi|}: Used for SIGCHI conference articles.
\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
\end{itemize}

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, there are a number of {\itshape template parameters}
which modify some part of the applied template style. A complete list
of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
  conference submission. Anonymizes the work and includes line
  numbers. Use with the \verb|\acmSubmissionID| command to print the
  submission's unique ID on each page of the work.
\item{\verb|authorversion|}: Produces a version of the work suitable
  for posting by the author.
\item{\verb|screen|}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the
source file:
\begin{verbatim}
\documentclass[sigconf]{acmart}
\end{verbatim}

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

{\bfseries Your document will be returned to you for revision if
  modifications are discovered.}

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

\section{Title Information}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the {\verb|title|} command to define the title of
your work. If your work has a subtitle, define it with the
{\verb|subtitle|} command.  Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used
in the page headers, to prevent overlapping text. The \verb|title|
command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification. Multiple authors may share one affiliation. Authors'
names should not be abbreviated; use full first names wherever
possible. Include authors' e-mail addresses whenever possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

Note that authors' addresses are mandatory for journal articles.

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

The ACM Reference Format text is required for all articles over one
page in length, and is optional for one-page articles (abstracts).

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful
taxonomic tools for you to help readers find your work in an online
search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing
discipline. Authors can select entries from this classification
system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases
of the authors' choosing, providing a more flexible way of describing
the research being presented.

CCS concepts and user-defined keywords are required for for all
articles over two pages in length, and are optional for one- and
two-page articles (or abstracts).

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands:
\verb|section|, \verb|subsection|, \verb|subsubsection|, and
\verb|paragraph|. They should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is {\bfseries not allowed.}

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}

Always use midrule to separate table header rows from data rows, and
use it only for this purpose. This enables assistive technologies to
recognise table headers and support their users in navigating tables
more easily.

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual
\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX\@; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{A woman and a girl in white dresses sit in an open car.}
\end{figure}

Your figures should contain a caption which describes the figure to
the reader.

Figure captions are placed {\itshape below} the figure.

Every figure should also have a figure description unless it is purely
decorative. These descriptions convey what’s in the image to someone
who cannot see it. They are also used by search engine crawlers for
indexing images, and when images cannot be loaded.

A figure description must be unformatted plain text less than 2000
characters long (including spaces).  {\bfseries Figure descriptions
  should not repeat the figure caption – their purpose is to capture
  important information that is not already provided in the caption or
  the main text of the paper.} For figures that convey important and
complex new information, a short text description may not be
adequate. More complex alternative descriptions can be placed in an
appendix and referenced in a short figure description. For example,
provide a data table capturing the information in a bar chart, or a
structured list representing a graph.  For additional information
regarding how best to write figure descriptions and why doing this is
so important, please see
\url{https://www.acm.org/publications/taps/describing-figures/}.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the \BibTeX\ file.

Citations and references are numbered by default. A small number of
ACM publications have citations and references formatted in the
``author year'' style; for these exceptions, please include this
command in the {\bfseries preamble} (before the command
``\verb|\begin{document}|'') of your \LaTeX\ source:
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

  Some examples.  A paginated journal article \cite{Abril07}, an
  enumerated journal article \cite{Cohen07}, a reference to an entire
  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
  monograph/whole book in a series (see 2a in spec. document)
  \cite{Harel79}, a divisible-book such as an anthology or compilation
  \cite{Editor00} followed by the same example, however we only output
  the series if the volume number is given \cite{Editor00a} (so
  Editor00a's series should NOT be present since it has no vol. no.),
  a chapter in a divisible book \cite{Spector90}, a chapter in a
  divisible book in a series \cite{Douglass98}, a multi-volume work as
  book \cite{Knuth97}, a couple of articles in a proceedings (of a
  conference, symposium, workshop for example) (paginated proceedings
  article) \cite{Andler79, Hagerup1993}, a proceedings article with
  all possible elements \cite{Smith10}, an example of an enumerated
  proceedings article \cite{VanGundy07}, an informally published work
  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
  master's thesis: \cite{anisi03}, an online document / world wide web
  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
  publication \cite{rous08}, 'YYYYb'-test for prolific author
  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
  contain 'duplicate' DOI and URLs (some SIAM articles)
  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
  couple of citations with DOIs:
  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
  \cite{R} and \cite{UMassCitations}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not
numbered. This document has two appendices, demonstrating the section
and subsection identification method.

\section{SIGCHI Extended Abstracts}

The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
not in Word) produces a landscape-orientation formatted article, with
a wide left margin. Three environments are available for use with the
``\verb|sigchi-a|'' template style, and produce formatted output in
the margin:
\begin{itemize}
\item {\verb|sidebar|}:  Place formatted text in the margin.
\item {\verb|marginfigure|}: Place a figure in the margin.
\item {\verb|margintable|}: Place a table in the margin.
\end{itemize}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.

### 2021-01-28 article/tex/submission.tex
adds structure of the article

@@
 %% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
-  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
-\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
-  June 03--05, 2018, Woodstock, NY}
+\acmConference[Woodstock '18]{Woodstock '18: ACM International Conference of Human-Robot Interaction}{8 March 2021}{Online}
+\acmBooktitle{Woodstock '18: ACM International Conference of Human-Robot Interaction,
+8 March 2021, Online}
 \acmPrice{15.00}
@@
 
+\author{Co-author A}
+\affiliation{%
+  \institution{University of A}
+  \streetaddress{Adress}
+  \city{City}
+  \country{Country}}
+\email{email@internet.org}
+
+\author{Co-author B}
+\affiliation{%
+\institution{University of A}
+\streetaddress{Adress}
+\city{City}
+\country{Country}}
+\email{email@internet.org}
+
 \author{Miguel Xochicale}
@@
 
-\author{John Smith}
-\affiliation{%
-  \institution{The Th{\o}rv{\"a}ld Group}
-  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
-  \city{Hekla}
-  \country{Iceland}}
-\email{jsmith@affiliation.org}
-
-\author{Julius P. Kumquat}
-\affiliation{%
-  \institution{The Kumquat Consortium}
-  \city{New York}
-  \country{USA}}
-\email{jpkumquat@consortium.net}
-
 %%
@@
 %% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Trovato and Tobin, et al.}
+\renewcommand{\shortauthors}{Xochicale M. et al.}
 
@@
 \begin{abstract}
+  A clear and well-documented \LaTeX\ document is presented as an
+  article formatted for publication by ACM in a conference proceedings
+  or journal publication. Based on the ``acmart'' document class, this
+  article presents and explains many of the common variations, as well
+  as many of the formatting elements an author may use in the
+  preparation of the documentation of their work.
   A clear and well-documented \LaTeX\ document is presented as an
@@
      <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+         <concept_id>10003120.10003121.10011748</concept_id>
+         <concept_desc>Human-centered computing~Empirical studies in HCI</concept_desc>
          <concept_significance>500</concept_significance>
@@
      <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
+         <concept_id>10003120.10011738.10011776</concept_id>
+         <concept_desc>Human-centered computing~Accessibility systems and tools</concept_desc>
+         <concept_significance>500</concept_significance>
+         </concept>
+     <concept>
+         <concept_id>10010405.10010489.10010491</concept_id>
+         <concept_desc>Applied computing~Interactive learning environments</concept_desc>
          <concept_significance>300</concept_significance>
@@
      <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
+         <concept_id>10003456.10010927.10010930.10010931</concept_id>
+         <concept_desc>Social and professional topics~Children</concept_desc>
+         <concept_significance>500</concept_significance>
          </concept>
      <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
+         <concept_id>10010147.10010178.10010187.10010194</concept_id>
+         <concept_desc>Computing methodologies~Cognitive robotics</concept_desc>
+         <concept_significance>300</concept_significance>
          </concept>
@@
 
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
+\ccsdesc[500]{Human-centered computing~Empirical studies in HCI}
+\ccsdesc[500]{Human-centered computing~Accessibility systems and tools}
+\ccsdesc[300]{Applied computing~Interactive learning environments}
+\ccsdesc[500]{Social and professional topics~Children}
+\ccsdesc[300]{Computing methodologies~Cognitive robotics}
 
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{datasets, neural networks, gaze detection, text tagging}
+\keywords{Child-robot interaction, child-centred AI, Educational Robotics}
 
@@
 \section{Introduction}
+
+Current progress in the fields of Artificial Intelligence and Robotics (AIR)
+is accelerating specially in countries where innonavtion and technologies are happenigs. 
+However, even thought these fields are growing work is in progress in separated streams
+for AI and Robotics, there is little work that put together both fields and with
+little to none focus on children. With this in mind this work is proposing 
+the term AIR4children in a way to offer pedagogical, open-source software and hardware
+tools to balance the current posiblities for children to enjoy and to dicover these 
+fields from a children-like perspective.
+As pointed in the guidance of AI for children by UNICEF \cite{UNICEF2020},
+there are many challenges to make inclusive AIR, in this case, 
+from any or idealialy under-represented communities and provie fairness and non-discrimination 
+in child-robot interaction as well as design curriculums for children of different 
+socieconomical backgrounds, developmental stages or learning abilitities. 
+The aim of the AIR4children is to prepare children for present 
+to contribute to resposnbile AIR for the present and the future.
+
+Anoother aspects as the socialbitly of robots are well explamplied with 
+Jibo [REF], Cosmos [REF] and more recently Shelly, a tortoise-like robot, to tacke 
+multiple interaction of one-to-many as well the resctrition of children
+abusive behaviours towards robots \cite{hu2018}.
+
 ACM's consolidated article template, introduced in 2017, provides a
+
 consistent \LaTeX\ style for use across ACM publications, and
@@
 
-\section{Template Overview}
+\section{Open Source AI and Robotics}
 As noted in the introduction, the ``\verb|acmart|'' document class can
@@
 
-\subsection{Template Styles}
+\subsection{Open Source AI}
+As noted in the introduction, the ``\verb|acmart|'' document class can
+be used to prepare many different kinds of documentation --- a
+double-blind initial submission of a full-length technical paper, a
+two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
+journal article, a SIGCHI Extended Abstract, and more --- all by
+selecting the appropriate {\itshape template style} and {\itshape
+  template parameters}.
 
-The primary parameter given to the ``\verb|acmart|'' document class is
-the {\itshape template style} which corresponds to the kind of publication
-or SIG publishing the work. This parameter is enclosed in square
-brackets and is a part of the {\verb|documentclass|} command:
-\begin{verbatim}
-  \documentclass[STYLE]{acmart}
-\end{verbatim}
+\subsection{Open Source Robotics}
+As noted in the introduction, the ``\verb|acmart|'' document class can
+be used to prepare many different kinds of documentation --- a
+double-blind initial submission of a full-length technical paper, a
+two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
+journal article, a SIGCHI Extended Abstract, and more --- all by
+selecting the appropriate {\itshape template style} and {\itshape
+  template parameters}.
 
-Journals use one of three template styles. All but three ACM journals
-use the {\verb|acmsmall|} template style:
-\begin{itemize}
-\item {\verb|acmsmall|}: The default journal template style.
-\item {\verb|acmlarge|}: Used by JOCCH and TAP.
-\item {\verb|acmtog|}: Used by TOG.
-\end{itemize}
-
-The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
-\begin{itemize}
-\item {\verb|acmconf|}: The default proceedings template style.
-\item{\verb|sigchi|}: Used for SIGCHI conference articles.
-\item{\verb|sigchi-a|}: Used for SIGCHI ``Extended Abstract'' articles.
-\item{\verb|sigplan|}: Used for SIGPLAN conference articles.
-\end{itemize}
-
-\subsection{Template Parameters}
-
-In addition to specifying the {\itshape template style} to be used in
-formatting your work, there are a number of {\itshape template parameters}
-which modify some part of the applied template style. A complete list
-of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}
-
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-\item {\verb|anonymous,review|}: Suitable for a ``double-blind''
-  conference submission. Anonymizes the work and includes line
-  numbers. Use with the \verb|\acmSubmissionID| command to print the
-  submission's unique ID on each page of the work.
-\item{\verb|authorversion|}: Produces a version of the work suitable
-  for posting by the author.
-\item{\verb|screen|}: Produces colored hyperlinks.
-\end{itemize}
-
-This document uses the following string as the first command in the
-source file:
-\begin{verbatim}
-\documentclass[sigconf]{acmart}
-\end{verbatim}
-
-\section{Modifications}
-
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
-
-{\bfseries Your document will be returned to you for revision if
-  modifications are discovered.}
-
-\section{Typefaces}
-
-The ``\verb|acmart|'' document class requires the use of the
-``Libertine'' typeface family. Your \TeX\ installation should include
-this set of packages. Please do not substitute other typefaces. The
-``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
-as they will override the built-in typeface families.
-
-\section{Title Information}
-
-The title of your work should use capital letters appropriately -
-\url{https://capitalizemytitle.com/} has useful rules for
-capitalization. Use the {\verb|title|} command to define the title of
-your work. If your work has a subtitle, define it with the
-{\verb|subtitle|} command.  Do not insert line breaks in your title.
-
-If your title is lengthy, you must define a short version to be used
-in the page headers, to prevent overlapping text. The \verb|title|
-command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
-
-\section{Authors and Affiliations}
-
-Each author must be defined separately for accurate metadata
-identification. Multiple authors may share one affiliation. Authors'
-names should not be abbreviated; use full first names wherever
-possible. Include authors' e-mail addresses whenever possible.
-
-Grouping authors' names or e-mail addresses, or providing an ``e-mail
-alias,'' as shown below, is not acceptable:
-\begin{verbatim}
-  \author{Brooke Aster, David Mehldau}
-  \email{dave,judy,steve@university.edu}
-  \email{firstname.lastname@phillips.org}
-\end{verbatim}
-
-The \verb|authornote| and \verb|authornotemark| commands allow a note
-to apply to multiple authors --- for example, if the first two authors
-of an article contributed equally to the work.
-
-If your author list is lengthy, you must define a shortened version of
-the list of authors to be used in the page headers, to prevent
-overlapping text. The following command should be placed just after
-the last \verb|\author{}| definition:
-\begin{verbatim}
-  \renewcommand{\shortauthors}{McCartney, et al.}
-\end{verbatim}
-Omitting this command will force the use of a concatenated list of all
-of the authors' names, which may result in overlapping text in the
-page headers.
-
-The article template's documentation, available at
-\url{https://www.acm.org/publications/proceedings-template}, has a
-complete explanation of these commands and tips for their effective
-use.
-
-Note that authors' addresses are mandatory for journal articles.
-
-\section{Rights Information}
-
-Authors of any work published by ACM will need to complete a rights
-form. Depending on the kind of work, and the rights management choice
-made by the author, this may be copyright transfer, permission,
-license, or an OA (open access) agreement.
-
-Regardless of the rights management choice, the author will receive a
-copy of the completed rights form once it has been submitted. This
-form contains \LaTeX\ commands that must be copied into the source
-document. When the document source is compiled, these commands and
-their parameters add formatted text to several areas of the final
-document:
-\begin{itemize}
-\item the ``ACM Reference Format'' text on the first page.
-\item the ``rights management'' text on the first page.
-\item the conference information in the page header(s).
-\end{itemize}
-
-Rights information is unique to the work; if you are preparing several
-works for an event, make sure to use the correct set of commands with
-each of the works.
-
-The ACM Reference Format text is required for all articles over one
-page in length, and is optional for one-page articles (abstracts).
-
-\section{CCS Concepts and User-Defined Keywords}
-
-Two elements of the ``acmart'' document class provide powerful
-taxonomic tools for you to help readers find your work in an online
-search.
-
-The ACM Computing Classification System ---
-\url{https://www.acm.org/publications/class-2012} --- is a set of
-classifiers and concepts that describe the computing
-discipline. Authors can select entries from this classification
-system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
-commands to be included in the \LaTeX\ source.
-
-User-defined keywords are a comma-separated list of words and phrases
-of the authors' choosing, providing a more flexible way of describing
-the research being presented.
-
-CCS concepts and user-defined keywords are required for for all
-articles over two pages in length, and are optional for one- and
-two-page articles (or abstracts).
-
-\section{Sectioning Commands}
-
-Your work should use standard \LaTeX\ sectioning commands:
-\verb|section|, \verb|subsection|, \verb|subsubsection|, and
-\verb|paragraph|. They should be numbered; do not remove the numbering
-from the commands.
-
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is {\bfseries not allowed.}
-
-\section{Tables}
-
+\section{Open AIR4Children}
 The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
@@
 
-\section{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \textbf{math} environment,
-which can be invoked with the usual
-\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
-the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX\@; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
+\subsection{Open hardware and software}
 The ``\verb|figure|'' environment should be used for figures. One or
@@
 
-\subsection{The ``Teaser Figure''}
+\subsection{Open teaching materials}
 
@@
 
-\section{Citations and Bibliographies}
+\section{Conclusions and future work}
 
@@
 
-  Some examples.  A paginated journal article \cite{Abril07}, an
-  enumerated journal article \cite{Cohen07}, a reference to an entire
-  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
-  monograph/whole book in a series (see 2a in spec. document)
-  \cite{Harel79}, a divisible-book such as an anthology or compilation
-  \cite{Editor00} followed by the same example, however we only output
-  the series if the volume number is given \cite{Editor00a} (so
-  Editor00a's series should NOT be present since it has no vol. no.),
-  a chapter in a divisible book \cite{Spector90}, a chapter in a
-  divisible book in a series \cite{Douglass98}, a multi-volume work as
-  book \cite{Knuth97}, a couple of articles in a proceedings (of a
-  conference, symposium, workshop for example) (paginated proceedings
-  article) \cite{Andler79, Hagerup1993}, a proceedings article with
-  all possible elements \cite{Smith10}, an example of an enumerated
-  proceedings article \cite{VanGundy07}, an informally published work
-  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
-    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
-  master's thesis: \cite{anisi03}, an online document / world wide web
-  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
-  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
-  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
-  publication \cite{rous08}, 'YYYYb'-test for prolific author
-  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-  contain 'duplicate' DOI and URLs (some SIAM articles)
-  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-  couple of citations with DOIs:
-  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
-  \cite{R} and \cite{UMassCitations}.
+  Some examples.  A paginated journal article \cite{UNICEF2020}
+  %, an
+  %enumerated journal article \cite{Cohen07}, a reference to an entire
+  %issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
+  %monograph/whole book in a series (see 2a in spec. document).
+  %tech report: \cite{Harel78},
+  %online: \cite{Thornburg01},
+  %online: \cite{Ablamowicz07},
+  %misc: \cite{Poker06}
+  %misc: \cite{Obama08}
+  %manuals:  \cite{Fear05},
+  % \cite{Amsthm15}
 
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
-
-This section has a special environment:
-\begin{verbatim}
-  \begin{acks}
-  ...
-  \end{acks}
-\end{verbatim}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
-
-\section{Appendices}
-
-If your work needs an appendix, add it before the
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
-
-Start the appendix with the ``\verb|appendix|'' command:
-\begin{verbatim}
-  \appendix
-\end{verbatim}
-and note that in the appendix, sections are lettered, not
-numbered. This document has two appendices, demonstrating the section
-and subsection identification method.
-
-\section{SIGCHI Extended Abstracts}
-
-The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
-not in Word) produces a landscape-orientation formatted article, with
-a wide left margin. Three environments are available for use with the
-``\verb|sigchi-a|'' template style, and produce formatted output in
-the margin:
-\begin{itemize}
-\item {\verb|sidebar|}:  Place formatted text in the margin.
-\item {\verb|marginfigure|}: Place a figure in the margin.
-\item {\verb|margintable|}: Place a table in the margin.
-\end{itemize}
+%  \cite{Harel79}, a divisible-book such as an anthology or compilation
+%  \cite{Editor00} followed by the same example, however we only output
+%  the series if the volume number is given \cite{Editor00a} (so
+%  Editor00a's series should NOT be present since it has no vol. no.),
+%  a chapter in a divisible book \cite{Spector90}, a chapter in a
+%  divisible book in a series \cite{Douglass98}, a multi-volume work as
+%  book \cite{Knuth97}, a couple of articles in a proceedings (of a
+%  conference, symposium, workshop for example) (paginated proceedings
+%  article) \cite{Andler79, Hagerup1993}, a proceedings article with
+%  all possible elements \cite{Smith10}, an example of an enumerated
+%  proceedings article \cite{VanGundy07}, an informally published work
+%  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
+%    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
+%  master's thesis: \cite{anisi03}, an online document / world wide web
+% resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
+%  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
+%  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
+%  publication \cite{rous08}, 'YYYYb'-test for prolific author
+%  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
+%  contain 'duplicate' DOI and URLs (some SIAM articles)
+%  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
+%  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
+%  couple of citations with DOIs:
+%  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
+%  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
+%  \cite{R} and \cite{UMassCitations}.
 
@@
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{sample-base}
-
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
-
-\section{Research Methods}
-
-\subsection{Part One}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-lacinia dolor. Integer ultricies commodo sem nec semper.
-
-\subsection{Part Two}
-
-Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
-ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
-ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
-eros. Vivamus non purus placerat, scelerisque diam eu, cursus
-ante. Etiam aliquam tortor auctor efficitur mattis.
-
-\section{Online Resources}
-
-Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
-pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
-enim maximus. Vestibulum gravida massa ut felis suscipit
-congue. Quisque mattis elit a risus ultrices commodo venenatis eget
-dui. Etiam sagittis eleifend elementum.
-
-Nam interdum magna at lectus dignissim, ac dignissim lorem
-rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
-massa et mattis lacinia.
+\bibliography{../references/references}
 

### 2021-01-31 article/tex/submission.tex
polishes sections and adds references

@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{air4children: Artificial Intelligence and Robotics for Children}
-
+\title{AIR4children: Artificial Intelligence and Robotics for Children}
 %%
@@
 
-\author{Miguel Xochicale}
+\author{Co-author C}
 \affiliation{%
-  \institution{King's College London}
-  \city{London}
-  \country{UK}}
+  \institution{University}
+  \city{City}
+  \country{Country}}
 \authornotemark[1]
-\email{miguel.xochicale@kcl.ac.uk}
+\email{e@mail.com}
 
@@
 %% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Xochicale M. et al.}
+\renewcommand{\shortauthors}{Lastname et al.}
 
@@
 \begin{abstract}
-  A clear and well-documented \LaTeX\ document is presented as an
-  article formatted for publication by ACM in a conference proceedings
-  or journal publication. Based on the ``acmart'' document class, this
-  article presents and explains many of the common variations, as well
-  as many of the formatting elements an author may use in the
-  preparation of the documentation of their work.
-  A clear and well-documented \LaTeX\ document is presented as an
-  article formatted for publication by ACM in a conference proceedings
-  or journal publication. Based on the ``acmart'' document class, this
-  article presents and explains many of the common variations, as well
-  as many of the formatting elements an author may use in the
-  preparation of the documentation of their work.
+  In this work, we proposed air4children, artificial intelligence for children as a way to both (a) tackle aspect for inclusion and non-discrimination, agency, privacy, dignity, transparency, equity, fairness and participation and (b) child-centre approach for AI and robotics.
+  We introduce the present current challenges and opportunities for a child-centre approach for AI and robotics. 
+  Similarly, we touch on open-sourced software and hardware technologigies to make a more inclusive, transparent and fair participation of children in areas of AIR. 
+  Then, we describe the avenues that air4children can work with as development of open-sourced software and hardware, open-sourced teaching material. 
+  Finally, we add conclusions and future work. 
 \end{abstract}
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{Child-robot interaction, child-centred AI, Educational Robotics}
+\keywords{Child-centred AI, Educational Robotics, Child-robot interaction}
 
@@
 
-ACM's consolidated article template, introduced in 2017, provides a
-
-consistent \LaTeX\ style for use across ACM publications, and
-incorporates accessibility and metadata-extraction functionality
-necessary for future Digital Library endeavors. Numerous ACM and
-SIG-specific \LaTeX\ templates have been examined, and their unique
-features incorporated into this single new template.
-
-If you are new to publishing with ACM, this document is a valuable
-guide to the process of preparing your work for publication. If you
-have published with ACM before, this document provides insight and
-instruction into more recent changes to the article template.
-
-The ``\verb|acmart|'' document class can be used to prepare articles
-for any ACM publication --- conference or journal, and for any stage
-of publication, from review to final ``camera-ready'' copy, to the
-author's own version, with {\itshape very} few changes to the source.
-
 \section{Open Source AI and Robotics}
-As noted in the introduction, the ``\verb|acmart|'' document class can
-be used to prepare many different kinds of documentation --- a
-double-blind initial submission of a full-length technical paper, a
-two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
-journal article, a SIGCHI Extended Abstract, and more --- all by
-selecting the appropriate {\itshape template style} and {\itshape
-  template parameters}.
+The spirit of open source software since 19XX with the contributions 
+of users of different skills made a culture of openly share code to make
+more robust tools (i.e. firefox, ubuntu, etc). Much recently, something 
+similar to software is happening for hardware. One example is the community 
+for arduino that open-sourced diagrams, code and with a low-cost microcontroller
+magaged to make wordwile impact.
 
@@
 \begin{table}
-  \caption{Frequency of Special Characters}
+  \caption{Open source projects}
   \label{tab:freq}
@@
     \toprule
-    Non-English or Math&Frequency&Comments\\
+    Project name& Year of creation & Community\\
     \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
+    JetBot AI Robot \cite{nanoJetBot:2019} & March 2019 & - \\
+    JPL Open Source Rover \cite{OSR:2018} & April 2018 & - \\
+    Otto DIY robots \cite{OttoDIY:2016} & 2016 & 50K used robots in >70 countries\\
     $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
@@
 \end{table}
-
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-Always use midrule to separate table header rows from data rows, and
-use it only for this purpose. This enables assistive technologies to
-recognise table headers and support their users in navigating tables
-more easily.
 
@@
 
+Serholt 2017 performed studies to quantify the social intereaction 
+between robots and children (i.e., gaze, verbal interaction, gestures, 
+and facial expressions). However robotics tutors are not yet to the point 
+to deal with complex child-robot interactions. 
+\cite{Serholt:2017}
 A ``teaser figure'' is an image, or set of images in one figure, that

### 2021-01-31 article/tex/submission.tex
adds description of sections

@@
 for arduino that open-sourced diagrams, code and with a low-cost microcontroller
-magaged to make wordwile impact.
+magaged to make wordwile impact. See ~\ref{tab:opensourceprojects}.
 
@@
 \subsection{Open Source AI}
+[Section to describe open-source AI projects and related them to air4children].
 As noted in the introduction, the ``\verb|acmart|'' document class can
@@
 \subsection{Open Source Robotics}
+[Section to describe open-source robotics projects and related them to air4children.]
 As noted in the introduction, the ``\verb|acmart|'' document class can
@@
 \section{Open AIR4Children}
+[Section to describe the proposed project of air4children and the integration 
+of opensource tools.]
 The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
@@
   \caption{Open source projects}
-  \label{tab:freq}
+  \label{tab:opensourceprojects}
   \begin{tabular}{ccl}
@@
 \subsection{Open hardware and software}
+[Section to describe the hardware and software that can be used in 
+air4children.]
 The ``\verb|figure|'' environment should be used for figures. One or
@@
 \subsection{Open teaching materials}
-
+[Section to describe open teaching materials, perhaps using non-traditional education systems.]
 Serholt 2017 performed studies to quantify the social intereaction 
@@
 \section{Conclusions and future work}
-
+[for conclusions and future work].
 The use of \BibTeX\ for the preparation and formatting of one's

### 2021-02-03 article/tex/submission.tex
polishes introduction; adds references, air4children-v00 figure

@@
 \affiliation{%
-\institution{University of A}
+\institution{University of B}
 \streetaddress{Adress}
@@
 \begin{teaserfigure}
-  \includegraphics[width=\textwidth]{sampleteaser}
-  \caption{Seattle Mariners at Spring Training, 2010.}
-  \Description{Enjoying the baseball game from the third-base
-  seats. Ichiro Suzuki preparing to bat.}
+  \includegraphics[width=\textwidth]{../figures/air4children/versions/drawing-v00.png}
+  \caption{(a)open-source software and hardware, (b) non-traditional curriculums, (c) free for anyone.}
+  \Description{Enjoying the baseball game from the third-base seats. Ichiro Suzuki preparing to bat.}
   \label{fig:teaser}
@@
 \section{Introduction} 
-
-Current progress in the fields of Artificial Intelligence and Robotics (AIR)
-is accelerating specially in countries where innonavtion and technologies are happenigs. 
-However, even thought these fields are growing work is in progress in separated streams
-for AI and Robotics, there is little work that put together both fields and with
-little to none focus on children. With this in mind this work is proposing 
-the term AIR4children in a way to offer pedagogical, open-source software and hardware
-tools to balance the current posiblities for children to enjoy and to dicover these 
-fields from a children-like perspective.
-As pointed in the guidance of AI for children by UNICEF \cite{UNICEF2020},
-there are many challenges to make inclusive AIR, in this case, 
-from any or idealialy under-represented communities and provie fairness and non-discrimination 
-in child-robot interaction as well as design curriculums for children of different 
-socieconomical backgrounds, developmental stages or learning abilitities. 
-The aim of the AIR4children is to prepare children for present 
-to contribute to resposnbile AIR for the present and the future.
-
-Anoother aspects as the socialbitly of robots are well explamplied with 
-Jibo [REF], Cosmos [REF] and more recently Shelly, a tortoise-like robot, to tacke 
-multiple interaction of one-to-many as well the resctrition of children
-abusive behaviours towards robots \cite{hu2018}.
+The scientific and techonlogical progress in the fields of Artificial Intelligence and Robotics (AIR) is rapdily moving forward over the past decade. 
+Advances in AIR are mainly in countries such as United States, China and Europe where support of such fields is part of their agenda \cite{Savage2020}. 
+As the fielfs of AIR are advancing at a great pace, there are opportunties to for more child-centered AIR and with various challenges for children in places where resources are scarse. 
+Recently, a drafted guidance of AI for children by UNICEF \cite{UNICEF2020} pointed out various challenges of making such filed avaiable to under-represented communities with the aim of providing fairness and non-discrimination.
+With this in mind this work is proposing Artificial Intelligence and Robotics for Children (AIR4children) as a way to create and to design tools based on open-sourced projects.
+Similarly, AIR4children is aiming to design curriculums with an non-traditional education approach for children of different socieconomical backgrounds, developmental stages or learning abilitities. 
+%Anoother aspects as the socialbitly of robots are well explamplied with 
+%Jibo [REF], Cosmos [REF] and more recently Shelly, a tortoise-like robot, to tacke 
+%multiple interaction of one-to-many as well the resctrition of children
+%abusive behaviours towards robots \cite{hu2018}.
 
@@
   template parameters}.
+
+  Deep Learning (DL) is a branch of machine learning in Artificial Intelligence
+  which essentially takes advantage of a huge datasets to train neural networks.
+  The great impact of DL in recent years is also because of improvements in 
+  hardware development and mainly because of open source tools and libraries \cite{matelabs2017}.
+  Additionally to that, there is a huge range of applications in areas such as robotics,
+  transportation, medicine and last but not least in education.
+  That said, we propose to use a raspberry pi, a $\pounds$30 board with
+  GNU/Linux OS, connected with a mini arduino board, $\pounds$2 board,  servomotors 
+  and pi camera in order to create a simple low-cost educational robot 
+  where children can learn the basics concepts of robotics and deep learning \cite{durr2015}.
 
@@
 \url{https://www.acm.org/publications/taps/describing-figures/}.
+
+Our primary aim for Libre Robotics is to build low-cost education robots 
+which will be helpful to teach many didactic activities where children 
+can interact with the robot and learn concepts of robotics, linear algebra, 
+machine learning, and deep learning.
+One example is the implementation of a low-cost robot with 
+convolutional neural networks that recognise six basic face emotions: 
+happy, sad, surprise, fear, anger and neutral \cite{ho2016, Ruiz-Garcia2016}.
+
+%
 

### 2021-02-08 article/tex/submission.tex
adds chios contributions to open teaching materials sections and two references

@@
 
-%
+\subsection{Open teaching materials}
+Considering the work of Maria Montessori who emphasized “the hand is the instrument of the mind.” \cite{montessori2013absorbent}. 
+That said, children must develop concentration to develop their learning skills. 
+For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
+It is through movement and repetition that the child gets experience, allowing him to internalize new concepts. 
+One potential way to develip such skills is the help of activities in engigering and robotics. 
+Engineering and robotics has demonstrated that young children can experience a range of cognitive and social benefits when these materials are approprietely introduced in development stages [add berg2018, Bers-Horn, 2010; Kazakoff-Bers, 2012)].
+Engineering tasks in robotics allow children to participate in creative explorations, develop fine motor skills and hand-eye coordination, engage in collaboration and teamwork \cite{elkin2014}.
+Similarly, the children development of grasping and understanding mathematical concepts such as number, size, and shape (Bers, 2012; Resnick et al., 1998).
 
-\subsection{Open teaching materials}
-[Section to describe open teaching materials, perhaps using non-traditional education systems.]
-Serholt 2017 performed studies to quantify the social intereaction 
-between robots and children (i.e., gaze, verbal interaction, gestures, 
-and facial expressions). However robotics tutors are not yet to the point 
-to deal with complex child-robot interactions. 
-\cite{Serholt:2017}
+In that way, air4children's workshop integrates various hands-on activities where the children will develop different intellectual and social skills to incorporate into other areas of their lives.
+More specifically, such workshops are based on several Montessori principles such as: moving from the simple to the complex, the concrete to the abstract, the familiar to the unfamiliar and the general to the specific, as well as a mixed age group, where children can learn from each other.
+For instance, Elkin et al. (2014) \cite{elkin2014} explained how Robotics can also provide a way to engage children in problem-solving. 
+Finding solutions together translate to social situations as well as it provides children with the foundations for decision making, logical reasoning, categorizing, analytical thinking, negotiation, and creativity.
+Children who think creatively are curious and open-minded, have a sense of wonder and joy in learning.
+
+Using a variety of teaching materials that combine theory and practice, our workshop has the goal to create experiences to build children’s confidence, develop creativity, teamwork and curiosity.
+
+%[Section to describe open teaching materials, perhaps using non-traditional education systems.]
+%Serholt 2017 performed studies to quantify the social intereaction 
+%between robots and children (i.e., gaze, verbal interaction, gestures, 
+%and facial expressions). However robotics tutors are not yet to the point 
+%to deal with complex child-robot interactions. 
+%\cite{Serholt:2017}
+
+\section{Conclusions and future work}
+[for conclusions and future work].
+The use of \BibTeX\ for the preparation and formatting of one's
+references is strongly recommended. Authors' names should be complete
+--- use full first names (``Donald E. Knuth'') not initials
+(``D. E. Knuth'') --- and the salient identifying features of a
+reference should be included: title, year, volume, number, pages,
+article DOI, etc.
 A ``teaser figure'' is an image, or set of images in one figure, that
@@
 \end{verbatim}
-
-\section{Conclusions and future work}
-[for conclusions and future work].
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
 

### 2021-02-09 article/tex/submission.tex
adds ElvaCorona contribution

@@
 \section{Open AIR4Children}
-[Section to describe the proposed project of air4children and the integration 
-of opensource tools.]
-The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed {\itshape above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and the
-table caption.  The contents of the table itself must go in the
-\textbf{tabular} environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.  Again,
-detailed instructions on \textbf{tabular} material are found in the
-\textit{\LaTeX\ User's Guide}.
+The general population, parents and children consider that Robotics is for people with a high IQ, engineers, complicated to learn, and too expensive, in one word, UNREACHABLE.
+We are working on changing this perception.
+AIR4CHILDREN proposes to bring Artificial Intelligence and Robotics (AIR) from laboratories to playgrounds, showing that robotics is intuitive, fun and accessible.  
+AIR4CHILDREN is focused on achieving that AIR be perceived as a “game” or like a recreational activity, similar to swim, ride a bike, do chemical experiments, play chess, that the child says things like: “I want to play AIR (Robotics)”, “dear Santa Claus my wish is that you bring me a Robotic set”, “friend let's play to build a robot”.
+AIR4CHILDREN seeks to implement open hardware and software, which represents for parents an economically and accessible activity for their children.  
+Formally, the AIR4CHILDREN project, in a first phase invites children, adolescents and young people to "play AIR" through calls to summer courses.   
+The groups are formed according to their ages.
+In these courses we use different game-based learning techniques [refs], they are taught Artificial Intelligence and Robotics (construction and programming).
+During these activities they are observed in order to: i) discover individual and team skills, ii) develop their talents, and iii) monitor their growth.  
+The programs and equipment used will be open, currently work with [refs], in section 3.1. looks more in detail.  
+In the second phase, the children who took the course  are invited to be part of an AIR team, which will have permanent meetings, and will work on specific projects to participate on IAR competition events.
+In this case the groups are formed according to their capabilities.
+On a third phase at least once a year we celebrate a public exposition, where the children talk with other children and their parents, showing their robots, sharing their experiences, and interacting between the public and the team so that the general population has a new perception of AIR.
+The pilot project is being implemented in Xicohtzinco, a town from Tlaxcala, Mexico, with a population of, [refs].
 

### 2021-02-09 article/tex/submission.tex
adds DonatoBadilloPerez contribution to the conclusions

@@
 \section{Conclusions and future work}
-[for conclusions and future work].
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-A ``teaser figure'' is an image, or set of images in one figure, that
-are placed after all author and affiliation information, and before
-the body of the article, spanning the page. If you wish to have such a
-figure in your article, place the command immediately before the
-\verb|\maketitle| command:
-\begin{verbatim}
-  \begin{teaserfigure}
-    \includegraphics[width=\textwidth]{sampleteaser}
-    \caption{figure caption}
-    \Description{figure description}
-  \end{teaserfigure}
-\end{verbatim}
+In our fast-evolving world towards technology is important to teach children what
+they are going to face when they grow up, unfortunately many children don’t have
+access to technology or the opportunity to learn about robotics and AI, and others,
+although they already know this type of technology, they don’t know how it works
+and how to create more of this technology which is really important towards the
+future. This project aims for that goal, create a free space where we can help
+children know and comprehend the functionality of Robotics and AI so they can
+obtain the best of it and create even more technology, with a positive impact in
+society, regardless of their opportunities or status, we believe that every children
+has the potential to learn and create.
 

### 2021-02-13 article/tex/submission.tex
polishes paper and adds references

--- 2021-02-08 article/tex/submission.tex
@@
 
-\author{Co-author A}
+\author{air4children}
 \affiliation{%
-  \institution{University of A}
-  \streetaddress{Adress}
-  \city{City}
-  \country{Country}}
-\email{email@internet.org}
+  %\institution{University of A}
+  %\streetaddress{Adress}
+  \city{Xicohtzinco}
+  \country{M\'exico}}
+%\authornotemark[1]
+\email{air4children@gmail.com}
 
-\author{Co-author B}
-\affiliation{%
-\institution{University of B}
-\streetaddress{Adress}
-\city{City}
-\country{Country}}
-\email{email@internet.org}
-
-\author{Co-author C}
-\affiliation{%
-  \institution{University}
-  \city{City}
-  \country{Country}}
-\authornotemark[1]
-\email{e@mail.com}
+%\author{Co-author C}
+%\affiliation{%
+%  \institution{University}
+%  \city{City}
+%  \country{Country}}
+%\authornotemark[1]
+%\email{e@mail.com}
 
@@
 \begin{abstract}
-  In this work, we proposed air4children, artificial intelligence for children as a way to both (a) tackle aspect for inclusion and non-discrimination, agency, privacy, dignity, transparency, equity, fairness and participation and (b) child-centre approach for AI and robotics.
+In this work, we proposed air4children, artificial intelligence for children as a way to both (a) tackle aspects for inclusion, accesibility, transparency, equity, fairness and participation and (b) to create a child-centre approach for AI and robotics.
 We introduce the present current challenges and opportunities for a child-centre approach for AI and robotics. 
@@
 
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
 \maketitle
@@
 \section{Introduction} 
-The scientific and techonlogical progress in the fields of Artificial Intelligence and Robotics (AIR) is rapdily moving forward over the past decade. 
-Advances in AIR are mainly in countries such as United States, China and Europe where support of such fields is part of their agenda \cite{Savage2020}. 
-As the fielfs of AIR are advancing at a great pace, there are opportunties to for more child-centered AIR and with various challenges for children in places where resources are scarse. 
-Recently, a drafted guidance of AI for children by UNICEF \cite{UNICEF2020} pointed out various challenges of making such filed avaiable to under-represented communities with the aim of providing fairness and non-discrimination.
-With this in mind this work is proposing Artificial Intelligence and Robotics for Children (AIR4children) as a way to create and to design tools based on open-sourced projects.
-Similarly, AIR4children is aiming to design curriculums with an non-traditional education approach for children of different socieconomical backgrounds, developmental stages or learning abilitities. 
-%Anoother aspects as the socialbitly of robots are well explamplied with 
-%Jibo [REF], Cosmos [REF] and more recently Shelly, a tortoise-like robot, to tacke 
-%multiple interaction of one-to-many as well the resctrition of children
-%abusive behaviours towards robots \cite{hu2018}.
+The scientific and techonlogical progress in the fields of Artificial Intelligence and Robotics (AIR) has been rapdily moving forward over the past decade, specially in countries such as United States, China and Europe where support of such fields is part of their agenda \cite{Savage2020}.
+However, such pupport brings other challenges such as the little to none focus on a centered AIR for children as well as the challenge of making the fields of AIR avaible to under-represented communities.
+In terms of a child-centered AIR, ...
+Similarly, such technologies are unreaachable to young audiences from under-represented communities as recently pointed out by United Nations Children's Fund (UNICEF) \cite{UNICEF2020}.
+That said, this work is proposing Artificial Intelligence and Robotics for Children (AIR4children) as a way to make AIR avaiable to young audiences with perhaps limited resources and to creation and design tools based on open-sourced projects to address fairness and accesibility.
+Additionally, AIR4children is aiming to design curriculums with an non-traditional education approach for children of different socieconomical backgrounds, developmental stages or learning abilitities.
 
-\section{Open Source AI and Robotics}
+For this work, section 2 review open source projects as a way to minise cost for hardware and software as the basis of the materal for air4children which is presented in section 3. 
+Then, we conclude with current status of AIR for children, open source materials for hardware, software and teaching and add few words on the future work as a way to mitigate few of the challenges cited above.
+
+\section{Open Source Projects in AI and Robotics}
 The spirit of open source software since 19XX with the contributions 
@@
 
-This document will explain the major features of the document
-class. For further information, the {\itshape \LaTeX\ User's Guide} is
-available from
-\url{https://www.acm.org/publications/proceedings-template}.
-
-\subsection{Open Source AI}
+\subsection{[Open Source AI]}
 [Section to describe open-source AI projects and related them to air4children].
@@
 journal article, a SIGCHI Extended Abstract, and more --- all by
-selecting the appropriate {\itshape template style} and {\itshape
-  template parameters}.
-
-  Deep Learning (DL) is a branch of machine learning in Artificial Intelligence
+selecting the appropriate {\itshape template style} and {\itshape template parameters}.
+[Deep Learning (DL) is a branch of machine learning in Artificial Intelligence
 which essentially takes advantage of a huge datasets to train neural networks.
@@
 where children can learn the basics concepts of robotics and deep learning \cite{durr2015}.
+]
 
-\subsection{Open Source Robotics}
+%BLURS
+%which will be helpful to teach many didactic activities where children 
+%can interact with the robot and learn concepts of robotics, linear algebra, 
+%machine learning, and deep learning.
+
+%One example is the implementation of a low-cost robot with convolutional neural networks that recognise six basic face emotions: 
+%happy, sad, surprise, fear, anger and neutral \cite{ho2016, Ruiz-Garcia2016}.
+
+\subsection{[Open Source Robotics]}
 [Section to describe open-source robotics projects and related them to air4children.]
-As noted in the introduction, the ``\verb|acmart|'' document class can
+[As noted in the introduction, the ``\verb|acmart|'' document class can
 be used to prepare many different kinds of documentation --- a
@@
 template parameters}.
+]
 
-\section{Open AIR4Children}
-[Section to describe the proposed project of air4children and the integration 
-of opensource tools.]
-The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed {\itshape above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and the
-table caption.  The contents of the table itself must go in the
-\textbf{tabular} environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.  Again,
-detailed instructions on \textbf{tabular} material are found in the
-\textit{\LaTeX\ User's Guide}.
+%Anoother aspects as the socialbitly of robots are well explamplied with 
+%Jibo [REF], Cosmos [REF] and more recently Shelly, a tortoise-like robot, to tacke 
+%multiple interaction of one-to-many as well the resctrition of children
+%abusive behaviours towards robots \cite{hu2018}.
 
 Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
+Table~\ref{tab:opensourceprojects} is included in the input file; compare the
 placement of the table here with the table in the printed output of
 this document.
-
 \begin{table}
+  \begin{tabular}{cc}
+    \toprule
+    Project name & Year of creation \\  %& Community\\
+    \midrule
+    JetBot AI Robot \cite{nanoJetBot:2019} & March 2019 \\ %& - \\
+    JPL Open Source Rover \cite{OSR:2018} & April 2018 \\%& - \\
+    Otto DIY robots \cite{OttoDIY:2016} & 2016 \\ %& 50K used robots in >70 countries\\
+  \bottomrule
+\end{tabular}
 \caption{Open source projects}
 \label{tab:opensourceprojects}
-  \begin{tabular}{ccl}
-    \toprule
-    Project name& Year of creation & Community\\
-    \midrule
-    JetBot AI Robot \cite{nanoJetBot:2019} & March 2019 & - \\
-    JPL Open Source Rover \cite{OSR:2018} & April 2018 & - \\
-    Otto DIY robots \cite{OttoDIY:2016} & 2016 & 50K used robots in >70 countries\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
 \end{table}
 
+\section{AIR4Children as a open source project}
+Having known the benefits of not only the lower price of open source projects but the increase of customisation and control of these, AIR4Children is therfore intending to adopt a similar journey along the lines of open source principles with the aim of making low-cost, customiseble and accesible tools for a child-centred AIR.
+That said, in a first phase, AIR4CHILDREN project will be piloting teaching materials with our open source robots and otto, a well known open source educational robot.  
+Then in a second phase, and with feedback of the pilots, teaching materials as well as the customisation of open source robots will be improved to polish a more centred-child curriculum of AIR. 
+On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops that will be free to all the particpants. 
+This inital phases of the project will help us to provide evidence of the impact of AIR in a children of different backgrounds and evaluate their perception on the fields of AI and Robotics.
+
+%% BLURS 
+%On a third phase at least once a year we celebrate a public exposition, where the children talk with other children and their parents, 
+%showing their robots, sharing their experiences, and interacting between the public and the team so that the general population 
+%has a new perception of AIR.
+
+%The pilot project is being implemented in Xicohtzinco, a town from Tlaxcala, Mexico, with a population of, [refs].
+%for children and adolescents in
+%In these courses we use different game-based learning techniques [refs], they are taught Artificial Intelligence and Robotics (construction and programming).   
+%The programs and equipment used will be open, currently work with [refs], in section 3.1. looks more in detail.  
+%In the second phase, the children who took the course  are invited to be part of an AIR team, 
+%which will have permanent meetings, and will work on specific projects to participate on IAR competition events.
+
+%to "play AIR" through calls to summer courses.   
+%The groups are formed according to their ages. 
+%In this case the groups are formed according to their capabilities.
+
+%Terefore with the help of open hardware, software and meaterilas, we prposed ...
+%The general population, parents and children consider that Robotics is for people with a high IQ, engineers, complicated to learn, 
+%and too expensive, in one word, 
+%We are working on changing this perception...
+%is focused on achieving that AIR be perceived as a “game” or like a recreational activity,
+% similar to swim, ride a bike, do chemical experiments, play chess, that the child says things like: 
+% “I want to play AIR (Robotics)”, “dear Santa Claus my wish is that you bring me a Robotic set”, “friend let's play to build a robot”.
+
 \subsection{Open hardware and software}
-[Section to describe the hardware and software that can be used in 
-air4children.]
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
+Considering previous references from the open source community, or perhaps other emerging ones, of not only AI and Robotics but also the ones for hardware and software, AIR4Children is aiming to make its resources accesible to young audiences \cite{UNICEF2020}.
+For instance, one additional goal of air4children is to build and to design low-cost education robots as a way to mitigate the hight prices of educational robots.
+Our initial prototype called ro-bit can recongnise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser} a).
+Another example is otto robot, a DIY educational robot based on arduino, servomotors and a scratch like interface to program the robot (Fig \ref{fig:teaser} b).
+
 \begin{figure}[h]
@@
   \Description{A woman and a girl in white dresses sit in an open car.}
+  \label{fig:car}
 \end{figure}
-
-Your figures should contain a caption which describes the figure to
-the reader.
-
-Figure captions are placed {\itshape below} the figure.
-
-Every figure should also have a figure description unless it is purely
-decorative. These descriptions convey what’s in the image to someone
-who cannot see it. They are also used by search engine crawlers for
-indexing images, and when images cannot be loaded.
-
-A figure description must be unformatted plain text less than 2000
-characters long (including spaces).  {\bfseries Figure descriptions
-  should not repeat the figure caption – their purpose is to capture
-  important information that is not already provided in the caption or
-  the main text of the paper.} For figures that convey important and
-complex new information, a short text description may not be
-adequate. More complex alternative descriptions can be placed in an
-appendix and referenced in a short figure description. For example,
-provide a data table capturing the information in a bar chart, or a
-structured list representing a graph.  For additional information
-regarding how best to write figure descriptions and why doing this is
-so important, please see
-\url{https://www.acm.org/publications/taps/describing-figures/}.
-
-Our primary aim for Libre Robotics is to build low-cost education robots 
-which will be helpful to teach many didactic activities where children 
-can interact with the robot and learn concepts of robotics, linear algebra, 
-machine learning, and deep learning.
-One example is the implementation of a low-cost robot with 
-convolutional neural networks that recognise six basic face emotions: 
-happy, sad, surprise, fear, anger and neutral \cite{ho2016, Ruiz-Garcia2016}.
 
@@
 One potential way to develip such skills is the help of activities in engigering and robotics. 
-Engineering and robotics has demonstrated that young children can experience a range of cognitive and social benefits when these materials are approprietely introduced in development stages [add berg2018, Bers-Horn, 2010; Kazakoff-Bers, 2012)].
+Engineering and robotics has demonstrated that young children can experience a range of cognitive and social benefits when these materials are approprietely introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012}.
 Engineering tasks in robotics allow children to participate in creative explorations, develop fine motor skills and hand-eye coordination, engage in collaboration and teamwork \cite{elkin2014}.
-Similarly, the children development of grasping and understanding mathematical concepts such as number, size, and shape (Bers, 2012; Resnick et al., 1998).
+Similarly, the children development of grasping and understanding mathematical concepts such as number, size, and shape \cite{bers2012, resnick1998}.
 
@@
 Finding solutions together translate to social situations as well as it provides children with the foundations for decision making, logical reasoning, categorizing, analytical thinking, negotiation, and creativity.
-Children who think creatively are curious and open-minded, have a sense of wonder and joy in learning.
 
-Using a variety of teaching materials that combine theory and practice, our workshop has the goal to create experiences to build children’s confidence, develop creativity, teamwork and curiosity.
+%Using a variety of teaching materials that combine theory and practice, our workshop has the goal to create experiences to build children’s confidence, develop creativity, teamwork and curiosity.
+%During these activities they are observed in order to: i) discover individual and team skills, ii) develop their talents, and iii) monitor their growth.
 
@@
 \section{Conclusions and future work}
-[for conclusions and future work].
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-A ``teaser figure'' is an image, or set of images in one figure, that
-are placed after all author and affiliation information, and before
-the body of the article, spanning the page. If you wish to have such a
-figure in your article, place the command immediately before the
-\verb|\maketitle| command:
-\begin{verbatim}
-  \begin{teaserfigure}
-    \includegraphics[width=\textwidth]{sampleteaser}
-    \caption{figure caption}
-    \Description{figure description}
-  \end{teaserfigure}
-\end{verbatim}
+We introducted the term air4project as a project with the aim to tackle aspects for inclusion, accesibility, transparency, equity, fairness and participation of children in the fields of AI and Robotics as well as to create a more child-centre approach for AI and Robotics.
+In this work, we also touched on the open source projects in AI and Robotics as a corner stone for air4children with the aim of minise cost of the materials and made customised eduational material.  
+Similarly, it has been presented the three phases for air4children for piloting, impleting and refiningg workshops for children in the age range between 6 to 14. 
+We also touched on the creation of curriclumns with Montesoty education, a non-traditional eduational approach to help young audienes to develiip skills such as think creatively with curisitty and open-minded as well as develop a have a sense of wonder and joy in learning.
 
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}| command:
-\begin{verbatim}
-  \bibliographystyle{ACM-Reference-Format}
-  \bibliography{bibfile}
-\end{verbatim}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the \BibTeX\ file.
+For future plans, in the coming year, we will complete the first round of eduational material for a child-centre AI and robotics where pilots, workshops and showcases are part of the 2021 and 2022 agenda.
 
-Citations and references are numbered by default. A small number of
-ACM publications have citations and references formatted in the
-``author year'' style; for these exceptions, please include this
-command in the {\bfseries preamble} (before the command
-``\verb|\begin{document}|'') of your \LaTeX\ source:
-\begin{verbatim}
-  \citestyle{acmauthoryear}
-\end{verbatim}
+%% BLURS 
+%Since children are going to learn and enter to this vast world of technology is in our responsibility to create open safe platforms and strategies where every children can enter and learn about AI, regardless of their personal situation, to avoid creating an “AI divide”.
+%To create a free safe space means the development and implementation of new AI policies focused on children, and the creation of digital public goods including open AI models, open software and so on.
+%In our fast-evolving world towards technology is important to teach children what they are going to face when they grow up, unfortunately many children don’t have access to technology or the opportunity to learn about robotics and AI, and others, although they already know this type of technology, they don’t know how it works and how to create more of this technology which is really important towards the future.
+%This project aims for that goal, create a free space where we can help children know and comprehend the functionality of Robotics and AI so they can obtain the best of it and create even more technology, with a positive impact in society, regardless of their opportunities or status, we believe that every children has the potential to learn and create.
 
-  Some examples.  A paginated journal article \cite{UNICEF2020}
-  %, an
-  %enumerated journal article \cite{Cohen07}, a reference to an entire
-  %issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
-  %monograph/whole book in a series (see 2a in spec. document).
-  %tech report: \cite{Harel78},
-  %online: \cite{Thornburg01},
-  %online: \cite{Ablamowicz07},
-  %misc: \cite{Poker06}
-  %misc: \cite{Obama08}
-  %manuals:  \cite{Fear05},
-  % \cite{Amsthm15}
-
-%  \cite{Harel79}, a divisible-book such as an anthology or compilation
-%  \cite{Editor00} followed by the same example, however we only output
-%  the series if the volume number is given \cite{Editor00a} (so
-%  Editor00a's series should NOT be present since it has no vol. no.),
-%  a chapter in a divisible book \cite{Spector90}, a chapter in a
-%  divisible book in a series \cite{Douglass98}, a multi-volume work as
-%  book \cite{Knuth97}, a couple of articles in a proceedings (of a
-%  conference, symposium, workshop for example) (paginated proceedings
-%  article) \cite{Andler79, Hagerup1993}, a proceedings article with
-%  all possible elements \cite{Smith10}, an example of an enumerated
-%  proceedings article \cite{VanGundy07}, an informally published work
-%  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
-%    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
-%  master's thesis: \cite{anisi03}, an online document / world wide web
-% resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
-%  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
-%  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
-%  publication \cite{rous08}, 'YYYYb'-test for prolific author
-%  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-%  contain 'duplicate' DOI and URLs (some SIAM articles)
-%  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-%  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-%  couple of citations with DOIs:
-%  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-%  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}. Artifacts:
-%  \cite{R} and \cite{UMassCitations}.
-
-%%
 %% The acknowledgments section is defined using the "acks" environment

### 2021-02-14 article/tex/submission.tex
polished and add references

@@
 
-%%
 %% The "title" command has an optional parameter,
@@
   \caption{(a)open-source software and hardware, (b) non-traditional curriculums, (c) free for anyone.}
-  \Description{Enjoying the baseball game from the third-base seats. Ichiro Suzuki preparing to bat.}
+  %\Description{}
   \label{fig:teaser}
@@
 
-\section{Open Source Projects in AI and Robotics}
-The spirit of open source software since 19XX with the contributions 
-of users of different skills made a culture of openly share code to make
-more robust tools (i.e. firefox, ubuntu, etc). Much recently, something 
-similar to software is happening for hardware. One example is the community 
-for arduino that open-sourced diagrams, code and with a low-cost microcontroller
-magaged to make wordwile impact. See ~\ref{tab:opensourceprojects}.
+\section{Open Source Software and Hardware for AI and Robotics}
+In 1978 Donald Knuth designed \TeX, typesetting system, which is a role model for open source projects where organisational phases of its development and the relative simple accesibilty to users were crucial to its success \cite{gaudeul2007}.
+Then, in 1983 Richard Stallman, with the fustration to not freely inspect, modify or share software, founded the GNU project to then create a GNU manifesto stating the fredom to run, study, copy, and make modifcation of software \cite{stallman1985}.
+That said, such projects were the corner stone of what is known as the Open Software Initiative, founded by Bruce Perens and Eric S.
+Raymond in 1998, stating that projects must be free redistributable, code must be available and distributable, modification must be allowed and many others \cite{brasseur2018}.
+Following a similar spirit that software can be used, studied, copied, modified, and redistributed without restriction, projects of open source hardware started to emerge in mid 2000s emerged (e.g., OpenCores, RepRap (3D printing), Arduino, Adafruit and SparkFun) \cite{pearce2013}.
 
-\subsection{[Open Source AI]}
-[Section to describe open-source AI projects and related them to air4children].
-As noted in the introduction, the ``\verb|acmart|'' document class can
-be used to prepare many different kinds of documentation --- a
-double-blind initial submission of a full-length technical paper, a
-two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
-journal article, a SIGCHI Extended Abstract, and more --- all by
-selecting the appropriate {\itshape template style} and {\itshape template parameters}.
-[Deep Learning (DL) is a branch of machine learning in Artificial Intelligence
-which essentially takes advantage of a huge datasets to train neural networks.
-The great impact of DL in recent years is also because of improvements in 
-hardware development and mainly because of open source tools and libraries \cite{matelabs2017}.
-Additionally to that, there is a huge range of applications in areas such as robotics,
-transportation, medicine and last but not least in education.
-That said, we propose to use a raspberry pi, a $\pounds$30 board with
-GNU/Linux OS, connected with a mini arduino board, $\pounds$2 board,  servomotors 
-and pi camera in order to create a simple low-cost educational robot 
-where children can learn the basics concepts of robotics and deep learning \cite{durr2015}.
-]
+In the last decade, another wave of scientific inovation has been emerging in the field of AI due to open source software framewoks (e.g.
+pytorch, tensorflow, etc.) and places to distrute these (e.g.
+GitHub, gitlab, bitbucket) \cite{matelabs2017}
+However, little has been seen accross the fields of AI and Robotics. 
+For instance, OTTO DIY is an educational open source robot founded in 2016 by Camilo Parra, the community of OTTO has more than 20,000 users from 20 countries and more than 100 re-designs of the robot \cite{OttoDIY:2016}.
+With regards to Robotics, the JPL Open Source Rover, created by eingeerers at NASA and initially released in April 2018, is a good reference as it is designed with detialed instructiosn for contrutrions for high school students and beyond, and technical specifications, 3D models, ensmabled instructions are fully avaiable \cite{OSR:2018}.
+Recently, engineers at NVIDIA in 2019, resleased nano JetBot as a affortable, education and fun platform  "to give the hands on experience needed to create entirely new AI projects" \cite{nanoJetBot:2019}.
+That said, there is room to create platforms to create educational resources to teach AI and robotics, as pointed by JetBot, in a more affordable, educatianal and fun characteristcs.
+Table~\ref{tab:opensourceprojects} summarises three open source projects with year of establisment and cost.
+
+%One example is the implementation of a low-cost robot with convolutional neural networks that recognise six basic face emotions: 
+%happy, sad, surprise, fear, anger and neutral \cite{ho2016, ruiz-garcia2016}.
+
+%[Deep Learning (DL) is a branch of machine learning in Artificial Intelligence
+%which essentially takes advantage of a huge datasets to train neural networks.
+%Additionally to that, there is a huge range of applications in areas such as robotics,
+%transportation, medicine and last but not least in education.
+%That said, we propose to use a raspberry pi, a $\pounds$30 board with
+%GNU/Linux OS, connected with a mini arduino board, $\pounds$2 board,  servomotors 
+%and pi camera in order to create a simple low-cost educational robot 
+%where children can learn the basics concepts of robotics and deep learning \cite{durr2015}.
+%]
 
@@
 
-%One example is the implementation of a low-cost robot with convolutional neural networks that recognise six basic face emotions: 
-%happy, sad, surprise, fear, anger and neutral \cite{ho2016, Ruiz-Garcia2016}.
-
-\subsection{[Open Source Robotics]}
-[Section to describe open-source robotics projects and related them to air4children.]
-[As noted in the introduction, the ``\verb|acmart|'' document class can
-be used to prepare many different kinds of documentation --- a
-double-blind initial submission of a full-length technical paper, a
-two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
-journal article, a SIGCHI Extended Abstract, and more --- all by
-selecting the appropriate {\itshape template style} and {\itshape
-template parameters}.
-]
-
 %Anoother aspects as the socialbitly of robots are well explamplied with 
@@
 
-Immediately following this sentence is the point at which
-Table~\ref{tab:opensourceprojects} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
+%Immediately following this sentence is the point at which
+%Table~\ref{tab:opensourceprojects} is included in the input file; compare the
+%placement of the table here with the table in the printed output of
+%this document.
+
 \begin{table}
-  \begin{tabular}{cc}
+  \begin{tabular}{ccc}
     \toprule
-    Project name & Year of creation \\  %& Community\\
+    Project & Established  & Cost\\
     \midrule
-    JetBot AI Robot \cite{nanoJetBot:2019} & March 2019 \\ %& - \\
-    JPL Open Source Rover \cite{OSR:2018} & April 2018 \\%& - \\
-    Otto DIY robots \cite{OttoDIY:2016} & 2016 \\ %& 50K used robots in >70 countries\\
+    JPL Open Source Rover \cite{OSR:2018} & April 2018  &  USD 2500.00 \\
+    JetBot AI Robot \cite{nanoJetBot:2019} & March 2019  & EUROS 212.00    \\
+    Otto DIY robots \cite{OttoDIY:2016} & 2016 &  EUROS 100.00  \\
+    Robot at air4children & 2021 & EUROS 100.00  \\
   \bottomrule
 \end{tabular}
-\caption{Open source projects}
+\caption{Open source projects for educational AI and Robotics}
 \label{tab:opensourceprojects}
@@
 Having known the benefits of not only the lower price of open source projects but the increase of customisation and control of these, AIR4Children is therfore intending to adopt a similar journey along the lines of open source principles with the aim of making low-cost, customiseble and accesible tools for a child-centred AIR.
-That said, in a first phase, AIR4CHILDREN project will be piloting teaching materials with our open source robots and otto, a well known open source educational robot.  
+
+In a first phase, air4children project will be piloting teaching materials with our open source robots and otto, a well known open source educational robot.  
 Then in a second phase, and with feedback of the pilots, teaching materials as well as the customisation of open source robots will be improved to polish a more centred-child curriculum of AIR. 
@@
 
-\subsection{Open hardware and software}
-Considering previous references from the open source community, or perhaps other emerging ones, of not only AI and Robotics but also the ones for hardware and software, AIR4Children is aiming to make its resources accesible to young audiences \cite{UNICEF2020}.
-For instance, one additional goal of air4children is to build and to design low-cost education robots as a way to mitigate the hight prices of educational robots.
-Our initial prototype called ro-bit can recongnise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser} a).
-Another example is otto robot, a DIY educational robot based on arduino, servomotors and a scratch like interface to program the robot (Fig \ref{fig:teaser} b).
+\subsection{Open source hardware and software}
+Adpoting the philosophy of open source, air4children is aiming to tackle the need of accessible and affordable resources for AI and Robotics to young audiences \cite{UNICEF2020}.
+For instance, as a way to mitigate the hight prices of educational robots, our initial prototypes of air4children are in the range of EURO 100.00. 
+Such prototype, based on raspberry pi, arduino uno board and few actuators, is able to recongnise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser} a).
+Similarly, we have identified Otto robot, a DIY educational robot, which is based on arduino, servomotors and a scratch as interface to program the robot with various routines for sensors and actuators with a price of EURO 100.00 (Fig \ref{fig:teaser} b).
 
+\subsection{Open teaching materials}
+Propossing teaching materials be child-like oriented, air4children is adopting Montessori's education, who emphasized “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
+In that way, materials for air4children based on Montessori education with the aim to help children to internalise new concepts and to develop concentration on their learning skills through movement and repetition.
+%For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
+One potential way to develop such skills is by designing activities in AI and robotics with materials approprietely introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts such as number, size, and shape \cite{bers2012, resnick1998}.
+Similarly, Elkin et al.
+(2014) \cite{elkin2014}, for instance, explained how Robotics can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills and hand-eye coordination, engage in collaboration and teamwork.
+
+%Finding solutions together translate to social situations as well as it provides children with the foundations for decision making, logical reasoning, categorizing, analytical thinking, negotiation, and creativity.
+%In that way, air4children's workshop integrates various hands-on activities where the children will develop different intellectual and social skills to incorporate into other areas of their lives.
+%More specifically, such workshops are based on several Montessori principles such as: moving from the simple to the complex, the concrete to the abstract, the familiar to the unfamiliar and the general to the specific, as well as a mixed age group, where children can learn from each other.
 \begin{figure}[h]
@@
 \end{figure}
-
-\subsection{Open teaching materials}
-Considering the work of Maria Montessori who emphasized “the hand is the instrument of the mind.” \cite{montessori2013absorbent}. 
-That said, children must develop concentration to develop their learning skills. 
-For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
-It is through movement and repetition that the child gets experience, allowing him to internalize new concepts. 
-One potential way to develip such skills is the help of activities in engigering and robotics. 
-Engineering and robotics has demonstrated that young children can experience a range of cognitive and social benefits when these materials are approprietely introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012}.
-Engineering tasks in robotics allow children to participate in creative explorations, develop fine motor skills and hand-eye coordination, engage in collaboration and teamwork \cite{elkin2014}.
-Similarly, the children development of grasping and understanding mathematical concepts such as number, size, and shape \cite{bers2012, resnick1998}.
-
-In that way, air4children's workshop integrates various hands-on activities where the children will develop different intellectual and social skills to incorporate into other areas of their lives.
-More specifically, such workshops are based on several Montessori principles such as: moving from the simple to the complex, the concrete to the abstract, the familiar to the unfamiliar and the general to the specific, as well as a mixed age group, where children can learn from each other.
-For instance, Elkin et al. (2014) \cite{elkin2014} explained how Robotics can also provide a way to engage children in problem-solving. 
-Finding solutions together translate to social situations as well as it provides children with the foundations for decision making, logical reasoning, categorizing, analytical thinking, negotiation, and creativity.
 

### 2021-02-14 article/tex/submission.tex
adds figures and polishes open teaching materials

@@
 \begin{teaserfigure}
-  \includegraphics[width=\textwidth]{../figures/air4children/versions/drawing-v00.png}
-  \caption{(a)open-source software and hardware, (b) non-traditional curriculums, (c) free for anyone.}
+  \includegraphics[width=\textwidth]{../figures/air4children/versions/drawing-v01.png}
+  \caption{(a) Robot prototype (b) open-source robots for ai and robotics, (c) piloting teaching materials with children.}
   %\Description{}
@@
 For instance, as a way to mitigate the hight prices of educational robots, our initial prototypes of air4children are in the range of EURO 100.00. 
-Such prototype, based on raspberry pi, arduino uno board and few actuators, is able to recongnise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser} a).
-Similarly, we have identified Otto robot, a DIY educational robot, which is based on arduino, servomotors and a scratch as interface to program the robot with various routines for sensors and actuators with a price of EURO 100.00 (Fig \ref{fig:teaser} b).
+Such prototype, based on raspberry pi, arduino uno board and few actuators, is able to recongnise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser}(a)).
+Similarly, we have identified Otto robot, a DIY educational robot, which is based on arduino, servomotors and a scratch as interface to program the robot with various routines for sensors and actuators with a price of EURO 100.00 (Fig \ref{fig:tm} (b)).
 
 \subsection{Open teaching materials}
-Propossing teaching materials be child-like oriented, air4children is adopting Montessori's education, who emphasized “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
-In that way, materials for air4children based on Montessori education with the aim to help children to internalise new concepts and to develop concentration on their learning skills through movement and repetition.
+Considering teaching materials to be child-like oriented, air4children is then adopting Montessori's education which education philosophy orbited around this quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
+In that way, materials for air4children are based on Montessori education with the aim to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
 %For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
-One potential way to develop such skills is by designing activities in AI and robotics with materials approprietely introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts such as number, size, and shape \cite{bers2012, resnick1998}.
+One potential way to develop such skills is by designing activities in AI and robotics that are approprietely introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts (e.g.
+numbers, size, and shapes) \cite{bers2012, resnick1998}.
 Similarly, Elkin et al.
-(2014) \cite{elkin2014}, for instance, explained how Robotics can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills and hand-eye coordination, engage in collaboration and teamwork.
+(2014) \cite{elkin2014}, for instance, explained how Robotics can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.
+
+That said, figure \ref{fig:tm}(a) illustrate the spiral learning technique adoped for air4children to reinforce the above Montesory skills \cite{tarik2017}.
 
@@
   \centering
-  \includegraphics[width=\linewidth]{sample-franklin}
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-  \Description{A woman and a girl in white dresses sit in an open car.}
-  \label{fig:car}
+  \includegraphics[width=\linewidth]{../figures/teaching-materials/versions/drawing-v00.png}
+  \caption{(a) Spiral learnig divided into lecture, virtual and physical laboratory and connected via project to next session \cite{tarik2017} (b) robot assembly and (c) block-like programming style.}
+  %\Description{.}
+  \label{fig:tm}
 \end{figure}

### 2021-02-14 article/tex/submission.tex
spell checked

@@
 \begin{abstract}
-In this work, we proposed air4children, artificial intelligence for children as a way to both (a) tackle aspects for inclusion, accesibility, transparency, equity, fairness and participation and (b) to create a child-centre approach for AI and robotics.
+In this work, we proposed air4children, artificial intelligence for children as a way to both (a) tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation and (b) to create a child-centre approach for AI and robotics.
 We introduce the present current challenges and opportunities for a child-centre approach for AI and robotics. 
-Similarly, we touch on open-sourced software and hardware technologigies to make a more inclusive, transparent and fair participation of children in areas of AIR. 
+Similarly, we touch on open-sourced software and hardware technologies to make a more inclusive, transparent and fair participation of children in areas of AIR. 
 Then, we describe the avenues that air4children can work with as development of open-sourced software and hardware, open-sourced teaching material. 
@@
 \section{Introduction} 
-The scientific and techonlogical progress in the fields of Artificial Intelligence and Robotics (AIR) has been rapdily moving forward over the past decade, specially in countries such as United States, China and Europe where support of such fields is part of their agenda \cite{Savage2020}.
-However, such pupport brings other challenges such as the little to none focus on a centered AIR for children as well as the challenge of making the fields of AIR avaible to under-represented communities.
+The scientific and technological progress in the fields of Artificial Intelligence and Robotics (AIR) has been rapidly moving forward over the past decade, specially in countries such as United States, China and Europe where support of such fields is part of their agenda \cite{Savage2020}.
+However, such support brings other challenges such as the little to none focus on a centered AIR for children as well as the challenge of making the fields of AIR available to under-represented communities.
 In terms of a child-centered AIR, ...
-Similarly, such technologies are unreaachable to young audiences from under-represented communities as recently pointed out by United Nations Children's Fund (UNICEF) \cite{UNICEF2020}.
-That said, this work is proposing Artificial Intelligence and Robotics for Children (AIR4children) as a way to make AIR avaiable to young audiences with perhaps limited resources and to creation and design tools based on open-sourced projects to address fairness and accesibility.
-Additionally, AIR4children is aiming to design curriculums with an non-traditional education approach for children of different socieconomical backgrounds, developmental stages or learning abilitities.
+Similarly, such technologies are unreachable to young audiences from under-represented communities as recently pointed out by United Nations Children's Fund (UNICEF) \cite{UNICEF2020}.
+That said, this work is proposing Artificial Intelligence and Robotics for Children (AIR4children) as a way to make AIR available to young audiences with perhaps limited resources and to creation and design tools based on open-sourced projects to address fairness and accessibility.
+Additionally, AIR4children is aiming to design curriculums with an non-traditional education approach for children of different socio economical backgrounds, developmental stages or learning abilities.
 
-For this work, section 2 review open source projects as a way to minise cost for hardware and software as the basis of the materal for air4children which is presented in section 3. 
+For this work, section 2 review open source projects as a way to minimise cost for hardware and software as the basis of the material for air4children which is presented in section 3. 
 Then, we conclude with current status of AIR for children, open source materials for hardware, software and teaching and add few words on the future work as a way to mitigate few of the challenges cited above.
@@
 \section{Open Source Software and Hardware for AI and Robotics}
-In 1978 Donald Knuth designed \TeX, typesetting system, which is a role model for open source projects where organisational phases of its development and the relative simple accesibilty to users were crucial to its success \cite{gaudeul2007}.
-Then, in 1983 Richard Stallman, with the fustration to not freely inspect, modify or share software, founded the GNU project to then create a GNU manifesto stating the fredom to run, study, copy, and make modifcation of software \cite{stallman1985}.
+In 1978 Donald Knuth designed \TeX, typesetting system, which is a role model for open source projects where organisational phases of its development and the relative simple accessibility to users were crucial to its success \cite{gaudeul2007}.
+Then, in 1983 Richard Stallman, with the frustration to not freely inspect, modify or share software, founded the GNU project to then create a GNU manifesto stating the freedom to run, study, copy, and make modification of software \cite{stallman1985}.
 That said, such projects were the corner stone of what is known as the Open Software Initiative, founded by Bruce Perens and Eric S.
@@
 
-In the last decade, another wave of scientific inovation has been emerging in the field of AI due to open source software framewoks (e.g.
-pytorch, tensorflow, etc.) and places to distrute these (e.g.
+In the last decade, another wave of scientific innovation has been emerging in the field of AI due to open source software frameworks (e.g.
+pytorch, tensorflow, etc.) and places to distribute these (e.g.
 GitHub, gitlab, bitbucket) \cite{matelabs2017}
@@
 For instance, OTTO DIY is an educational open source robot founded in 2016 by Camilo Parra, the community of OTTO has more than 20,000 users from 20 countries and more than 100 re-designs of the robot \cite{OttoDIY:2016}.
-With regards to Robotics, the JPL Open Source Rover, created by eingeerers at NASA and initially released in April 2018, is a good reference as it is designed with detialed instructiosn for contrutrions for high school students and beyond, and technical specifications, 3D models, ensmabled instructions are fully avaiable \cite{OSR:2018}.
-Recently, engineers at NVIDIA in 2019, resleased nano JetBot as a affortable, education and fun platform  "to give the hands on experience needed to create entirely new AI projects" \cite{nanoJetBot:2019}.
-That said, there is room to create platforms to create educational resources to teach AI and robotics, as pointed by JetBot, in a more affordable, educatianal and fun characteristcs.
-Table~\ref{tab:opensourceprojects} summarises three open source projects with year of establisment and cost.
+With regards to Robotics, the JPL Open Source Rover, created by engineers at NASA and initially released in April 2018, is a good reference as it is designed with detailed instructions for constructions for high school students and beyond, and technical specifications, 3D models, assembly instructions are fully available \cite{OSR:2018}.
+Recently, engineers at NVIDIA in 2019, released nano JetBot as a affordable, education and fun platform  "to give the hands on experience needed to create entirely new AI projects" \cite{nanoJetBot:2019}.
+That said, there is room to create platforms to create educational resources to teach AI and robotics, as pointed by JetBot, in a more affordable, educational and fun characteristics.
+Table~\ref{tab:opensourceprojects} summarises three open source projects with year of establishment and cost.
 
@@
 \section{AIR4Children as a open source project}
-Having known the benefits of not only the lower price of open source projects but the increase of customisation and control of these, AIR4Children is therfore intending to adopt a similar journey along the lines of open source principles with the aim of making low-cost, customiseble and accesible tools for a child-centred AIR.
+Having known the benefits of not only the lower price of open source projects but the increase of customisation and control of these, AIR4Children is therefore intending to adopt a similar journey along the lines of open source principles with the aim of making low-cost, customisable and accessible tools for a child-centred AIR.
 
@@
 Then in a second phase, and with feedback of the pilots, teaching materials as well as the customisation of open source robots will be improved to polish a more centred-child curriculum of AIR. 
-On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops that will be free to all the particpants. 
-This inital phases of the project will help us to provide evidence of the impact of AIR in a children of different backgrounds and evaluate their perception on the fields of AI and Robotics.
+On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops that will be free to all the participants. 
+This initial phases of the project will help us to provide evidence of the impact of AIR in a children of different backgrounds and evaluate their perception on the fields of AI and Robotics.
 
@@
 \subsection{Open source hardware and software}
-Adpoting the philosophy of open source, air4children is aiming to tackle the need of accessible and affordable resources for AI and Robotics to young audiences \cite{UNICEF2020}.
+Adopting the philosophy of open source, air4children is aiming to tackle the need of accessible and affordable resources for AI and Robotics to young audiences \cite{UNICEF2020}.
 For instance, as a way to mitigate the hight prices of educational robots, our initial prototypes of air4children are in the range of EURO 100.00. 
-Such prototype, based on raspberry pi, arduino uno board and few actuators, is able to recongnise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser}(a)).
+Such prototype, based on raspberry pi, arduino uno board and few actuators, is able to recognise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser}(a)).
 Similarly, we have identified Otto robot, a DIY educational robot, which is based on arduino, servomotors and a scratch as interface to program the robot with various routines for sensors and actuators with a price of EURO 100.00 (Fig \ref{fig:tm} (b)).
@@
 %For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
-One potential way to develop such skills is by designing activities in AI and robotics that are approprietely introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts (e.g.
+One potential way to develop such skills is by designing activities in AI and robotics that are appropriately introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts (e.g.
 numbers, size, and shapes) \cite{bers2012, resnick1998}.
@@
 
-That said, figure \ref{fig:tm}(a) illustrate the spiral learning technique adoped for air4children to reinforce the above Montesory skills \cite{tarik2017}.
+That said, figure \ref{fig:tm}(a) illustrate the spiral learning technique adopted for air4children to reinforce the above Montessori skills \cite{tarik2017}.
 
@@
   \includegraphics[width=\linewidth]{../figures/teaching-materials/versions/drawing-v00.png}
-  \caption{(a) Spiral learnig divided into lecture, virtual and physical laboratory and connected via project to next session \cite{tarik2017} (b) robot assembly and (c) block-like programming style.}
+  \caption{(a) Spiral learning divided into lecture, virtual and physical laboratory and connected via project to next session \cite{tarik2017} (b) robot assembly and (c) block-like programming style.}
   %\Description{.}
@@
 \section{Conclusions and future work}
-We introducted the term air4project as a project with the aim to tackle aspects for inclusion, accesibility, transparency, equity, fairness and participation of children in the fields of AI and Robotics as well as to create a more child-centre approach for AI and Robotics.
-In this work, we also touched on the open source projects in AI and Robotics as a corner stone for air4children with the aim of minise cost of the materials and made customised eduational material.  
-Similarly, it has been presented the three phases for air4children for piloting, impleting and refiningg workshops for children in the age range between 6 to 14. 
-We also touched on the creation of curriclumns with Montesoty education, a non-traditional eduational approach to help young audienes to develiip skills such as think creatively with curisitty and open-minded as well as develop a have a sense of wonder and joy in learning.
+We introduced the term air4project as a project with the aim to tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation of children in the fields of AI and Robotics as well as to create a more child-centre approach for AI and Robotics.
+In this work, we also touched on the open source projects in AI and Robotics as a corner stone for air4children with the aim of minimise cost of the materials and made customised educational material.
+Similarly, it has been presented the three phases for air4children for piloting, implementing and refining workshops for children in the age range between 6 to 14. 
+We also touched on the creation of curriculums with Montessori education, a non-traditional educational approach to help young audiences to develop skills such as think creatively with curiosity and open-minded as well as develop a have a sense of wonder and joy in learning.
 
-For future plans, in the coming year, we will complete the first round of eduational material for a child-centre AI and robotics where pilots, workshops and showcases are part of the 2021 and 2022 agenda.
+For future plans, in the coming year, we will complete the first round of educational material for a child-centre AI and robotics where pilots, workshops and showcases are part of the 2021 and 2022 agenda.
 

### 2021-02-14 article/tex/submission.tex
polishes abstract

@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{AIR4children: Artificial Intelligence and Robotics for Children}
+\title{AIR4Children: Artificial Intelligence and Robotics for Children}
 %%
@@
 %% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Lastname et al.}
+\renewcommand{\shortauthors}{air4children}
 
@@
 \begin{abstract}
-In this work, we proposed air4children, artificial intelligence for children as a way to both (a) tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation and (b) to create a child-centre approach for AI and robotics.
-We introduce the present current challenges and opportunities for a child-centre approach for AI and robotics. 
+In this work, we proposed AIR4Children, artificial intelligence for children, as a way to (a) tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation and (b) to create affordable child-centred materials in AI and robotics.
+We present current challenges and opportunities for a child-centred approaches for AI and robotics (AIR). 
 Similarly, we touch on open-sourced software and hardware technologies to make a more inclusive, transparent and fair participation of children in areas of AIR. 
-Then, we describe the avenues that air4children can work with as development of open-sourced software and hardware, open-sourced teaching material. 
-Finally, we add conclusions and future work. 
+Then, we describe the avenues that AIR4Children can take with the development of open-sourced software and hardware.
+Similarly, we propose to follow the philosophy of Montessori education 
+to help children to not only develop matematical thinking but also to internalise new concepts and learning skills through activities of movement and repetition with open source robots.
+Finally, we add conclusions and mainly we pose the future work to go of AIR4children to putting in practice what is proposed here and measure the impact on AI and robotics of children. 
 \end{abstract}
@@
 Similarly, such technologies are unreachable to young audiences from under-represented communities as recently pointed out by United Nations Children's Fund (UNICEF) \cite{UNICEF2020}.
-That said, this work is proposing Artificial Intelligence and Robotics for Children (AIR4children) as a way to make AIR available to young audiences with perhaps limited resources and to creation and design tools based on open-sourced projects to address fairness and accessibility.
-Additionally, AIR4children is aiming to design curriculums with an non-traditional education approach for children of different socio economical backgrounds, developmental stages or learning abilities.
+That said, this work is proposing Artificial Intelligence and Robotics for Children (AIR4Children) as a way to make AIR available to young audiences with perhaps limited resources and to creation and design tools based on open-sourced projects to address fairness and accessibility.
+Additionally, AIR4Children is aiming to design curriculums with an non-traditional education approach for children of different socio economical backgrounds, developmental stages or learning abilities.
 
-For this work, section 2 review open source projects as a way to minimise cost for hardware and software as the basis of the material for air4children which is presented in section 3. 
+For this work, section 2 review open source projects as a way to minimise cost for hardware and software as the basis of the material for AIR4Children which is presented in section 3. 
 Then, we conclude with current status of AIR for children, open source materials for hardware, software and teaching and add few words on the future work as a way to mitigate few of the challenges cited above.
@@
     Otto DIY robots \cite{OttoDIY:2016} & 2016 &  EUROS 100.00  \\
-    Robot at air4children & 2021 & EUROS 100.00  \\
+    Robot at AIR4Children & 2021 & EUROS 100.00  \\
   \bottomrule
@@
 
-In a first phase, air4children project will be piloting teaching materials with our open source robots and otto, a well known open source educational robot.  
+In a first phase, AIR4Children project will be piloting teaching materials with our open source robots and otto, a well known open source educational robot.  
 Then in a second phase, and with feedback of the pilots, teaching materials as well as the customisation of open source robots will be improved to polish a more centred-child curriculum of AIR. 
@@
 \subsection{Open source hardware and software}
-Adopting the philosophy of open source, air4children is aiming to tackle the need of accessible and affordable resources for AI and Robotics to young audiences \cite{UNICEF2020}.
-For instance, as a way to mitigate the hight prices of educational robots, our initial prototypes of air4children are in the range of EURO 100.00. 
+Adopting the philosophy of open source, AIR4Children is aiming to tackle the need of accessible and affordable resources for AI and Robotics to young audiences \cite{UNICEF2020}.
+For instance, as a way to mitigate the hight prices of educational robots, our initial prototypes of AIR4Children are in the range of EURO 100.00. 
 Such prototype, based on raspberry pi, arduino uno board and few actuators, is able to recognise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser}(a)).
@@
 \subsection{Open teaching materials}
-Considering teaching materials to be child-like oriented, air4children is then adopting Montessori's education which education philosophy orbited around this quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
-In that way, materials for air4children are based on Montessori education with the aim to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
+Considering teaching materials to be child-like oriented, AIR4Children is then adopting Montessori's education which education philosophy orbited around this quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
+In that way, materials for AIR4Children are based on Montessori education with the aim to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
 %For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
@@
 
-That said, figure \ref{fig:tm}(a) illustrate the spiral learning technique adopted for air4children to reinforce the above Montessori skills \cite{tarik2017}.
+That said, figure \ref{fig:tm}(a) illustrate the spiral learning technique adopted for AIR4Children to reinforce the above Montessori skills \cite{tarik2017}.
 
 %Finding solutions together translate to social situations as well as it provides children with the foundations for decision making, logical reasoning, categorizing, analytical thinking, negotiation, and creativity.
-%In that way, air4children's workshop integrates various hands-on activities where the children will develop different intellectual and social skills to incorporate into other areas of their lives.
+%In that way, AIR4Children's workshop integrates various hands-on activities where the children will develop different intellectual and social skills to incorporate into other areas of their lives.
 %More specifically, such workshops are based on several Montessori principles such as: moving from the simple to the complex, the concrete to the abstract, the familiar to the unfamiliar and the general to the specific, as well as a mixed age group, where children can learn from each other.
@@
 We introduced the term air4project as a project with the aim to tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation of children in the fields of AI and Robotics as well as to create a more child-centre approach for AI and Robotics.
-In this work, we also touched on the open source projects in AI and Robotics as a corner stone for air4children with the aim of minimise cost of the materials and made customised educational material.
-Similarly, it has been presented the three phases for air4children for piloting, implementing and refining workshops for children in the age range between 6 to 14. 
+In this work, we also touched on the open source projects in AI and Robotics as a corner stone for AIR4Children with the aim of minimise cost of the materials and made customised educational material.
+Similarly, it has been presented the three phases for AIR4Children for piloting, implementing and refining workshops for children in the age range between 6 to 14. 
 We also touched on the creation of curriculums with Montessori education, a non-traditional educational approach to help young audiences to develop skills such as think creatively with curiosity and open-minded as well as develop a have a sense of wonder and joy in learning.

### 2021-02-14 article/tex/submission.tex
polished introduction

@@
 \section{Introduction} 
-The scientific and technological progress in the fields of Artificial Intelligence and Robotics (AIR) has been rapidly moving forward over the past decade, specially in countries such as United States, China and Europe where support of such fields is part of their agenda \cite{Savage2020}.
-However, such support brings other challenges such as the little to none focus on a centered AIR for children as well as the challenge of making the fields of AIR available to under-represented communities.
-In terms of a child-centered AIR, ...
-Similarly, such technologies are unreachable to young audiences from under-represented communities as recently pointed out by United Nations Children's Fund (UNICEF) \cite{UNICEF2020}.
-That said, this work is proposing Artificial Intelligence and Robotics for Children (AIR4Children) as a way to make AIR available to young audiences with perhaps limited resources and to creation and design tools based on open-sourced projects to address fairness and accessibility.
+The scientific and technological progress in the fields of Artificial Intelligence and Robotics (AIR) has been rapidly moving forward over the past decade with special focus in countries such as United States, China and Europe where support of such fields is part of their agenda \cite{Savage2020}.
+However, such progress also brings other challenges such as the little to none focus on a centred AIR for children as well as the challenge of making the fields of AIR available to under-represented communities.
+With regard to child-centered AIR, there is few materials and resources with poor accessble and not appropriately affortable.  
+In terms of affortability, such technologies are unreachable to young audiences from under-represented communities as recently pointed out by United Nations Children's Fund (UNICEF) \cite{UNICEF2020}.
+Therefore, this work is proposing Artificial Intelligence and Robotics for Children (AIR4Children) as a way to make AIR available to young audiences with perhaps limited resources and to creation and design tools based on open-sourced projects to address fairness and accessibility.
 Additionally, AIR4Children is aiming to design curriculums with an non-traditional education approach for children of different socio economical backgrounds, developmental stages or learning abilities.
 
-For this work, section 2 review open source projects as a way to minimise cost for hardware and software as the basis of the material for AIR4Children which is presented in section 3. 
-Then, we conclude with current status of AIR for children, open source materials for hardware, software and teaching and add few words on the future work as a way to mitigate few of the challenges cited above.
+For this work, as a way to minimise cost for hardware and software, section 2 review open source project as the basis of the material for AIR4Children.
+In section 3, it is presented three stages of AIR4Children including open source materials and teaching materials based on Montessori education. 
+We then conclude this work with current status of AIR for children, open source materials for hardware, software and teaching and add few words on the future work as a way to mitigate few of the challenges cited above.
 

### 2021-02-14 article/tex/submission.tex
poslishes section 2

@@
 \section{Open Source Software and Hardware for AI and Robotics}
-In 1978 Donald Knuth designed \TeX, typesetting system, which is a role model for open source projects where organisational phases of its development and the relative simple accessibility to users were crucial to its success \cite{gaudeul2007}.
-Then, in 1983 Richard Stallman, with the frustration to not freely inspect, modify or share software, founded the GNU project to then create a GNU manifesto stating the freedom to run, study, copy, and make modification of software \cite{stallman1985}.
-That said, such projects were the corner stone of what is known as the Open Software Initiative, founded by Bruce Perens and Eric S.
-Raymond in 1998, stating that projects must be free redistributable, code must be available and distributable, modification must be allowed and many others \cite{brasseur2018}.
+In 1978 Donald Knuth designed \TeX, typesetting system, which is a role model for open source projects where organisational phases of its development and the relative and simple accessibility to users were crucial to its success \cite{gaudeul2007}.
+Then, in 1983 Richard Stallman, with the frustration to not freely inspect, modify or share software, founded the GNU project to then create a GNU manifesto \cite{stallman1985}.
+Such projects were the corner stone of what is known as the Open Software Initiative, founded by Bruce Perens and Eric S.
+Raymond in 1998, stating that projects must be free redistributable, code must be available and distributable, modification must be allowed, etc \cite{brasseur2018}.
 Following a similar spirit that software can be used, studied, copied, modified, and redistributed without restriction, projects of open source hardware started to emerge in mid 2000s emerged (e.g., OpenCores, RepRap (3D printing), Arduino, Adafruit and SparkFun) \cite{pearce2013}.
 
-In the last decade, another wave of scientific innovation has been emerging in the field of AI due to open source software frameworks (e.g.
+Then, in the last decade, another wave of scientific innovation has been emerging in the field of AI due to open source software frameworks (e.g.
 pytorch, tensorflow, etc.) and places to distribute these (e.g.
-GitHub, gitlab, bitbucket) \cite{matelabs2017}
-However, little has been seen accross the fields of AI and Robotics. 
-For instance, OTTO DIY is an educational open source robot founded in 2016 by Camilo Parra, the community of OTTO has more than 20,000 users from 20 countries and more than 100 re-designs of the robot \cite{OttoDIY:2016}.
-With regards to Robotics, the JPL Open Source Rover, created by engineers at NASA and initially released in April 2018, is a good reference as it is designed with detailed instructions for constructions for high school students and beyond, and technical specifications, 3D models, assembly instructions are fully available \cite{OSR:2018}.
+GitHub, gitlab, bitbucket) \cite{matelabs2017}.
+However, little has been done for child-centred AI and Robotics. 
+For instance, Otto DIY is an educational open source robot founded in 2016 by Camilo Parra, where the community of OTTO has more than 20,000 users from 20 countries and more than 100 re-designs of the robot \cite{OttoDIY:2016}.
+Another example is the JPL Open Source Rover, created by engineers at NASA and initially released in April 2018, which it is designed with detailed instructions for constructions for mainly high school students, and open source technical specifications, 3D models and assembly instructions \cite{OSR:2018}.
 Recently, engineers at NVIDIA in 2019, released nano JetBot as a affordable, education and fun platform  "to give the hands on experience needed to create entirely new AI projects" \cite{nanoJetBot:2019}.
-That said, there is room to create platforms to create educational resources to teach AI and robotics, as pointed by JetBot, in a more affordable, educational and fun characteristics.
-Table~\ref{tab:opensourceprojects} summarises three open source projects with year of establishment and cost.
+
+That said, there is opportunity to create educational resources to teach AI and robotics to children aiming to be, as pointed by JetBot, affordable, educational and fun \cite{nanoJetBot:2019}, where our prototype is starting to tackle few of them.
+Table~\ref{tab:opensourceprojects} summarises open source projects with year of establishment and cost.
+
+%BLURS
 
@@
 
-%BLURS
 %which will be helpful to teach many didactic activities where children 

### 2021-02-14 article/tex/submission.tex
poslishes section 3

@@
 
-That said, there is opportunity to create educational resources to teach AI and robotics to children aiming to be, as pointed by JetBot, affordable, educational and fun \cite{nanoJetBot:2019}, where our prototype is starting to tackle few of them.
+That said, there is opportunity to create educational resources to teach AI and robotics to children aiming to be, as pointed by JetBot, affordable, educational and fun \cite{nanoJetBot:2019}, where our prototype, explained in next section, is starting to tackle few of them.
 Table~\ref{tab:opensourceprojects} summarises open source projects with year of establishment and cost.
@@
 
+\subsection{Open source hardware and software}
+Adopting the philosophy of open source, AIR4Children is aiming to tackle the need of accessible and affordable resources for AI and Robotics to young audiences \cite{UNICEF2020}.
+For instance, as a way to mitigate the hight prices of educational robots, our initial prototypes of AIR4Children are in the range of 100.00 EUROS. 
+Such prototype, based on raspberry pi, arduino uno board and few actuators, is able to recognise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser}(a)).
+Similarly, we have identified Otto robot, a DIY educational robot, which is based on arduino, servomotors and a scratch as interface to program the robot with various routines for sensors and actuators with a price of EURO 100.00 (Fig \ref{fig:tm} (b)).
+
 \section{AIR4Children as a open source project}
-Having known the benefits of not only the lower price of open source projects but the increase of customisation and control of these, AIR4Children is therefore intending to adopt a similar journey along the lines of open source principles with the aim of making low-cost, customisable and accessible tools for a child-centred AIR.
+Having known the benefits of not only the lower price of open source projects but the increase of customisation and control of these, AIR4Children is therefore intending to adopt a similar journey along the lines of open source principles with the aim of making affordable, customisable and accessible tools for a child-centred AIR.
 
-In a first phase, AIR4Children project will be piloting teaching materials with our open source robots and otto, a well known open source educational robot.  
-Then in a second phase, and with feedback of the pilots, teaching materials as well as the customisation of open source robots will be improved to polish a more centred-child curriculum of AIR. 
-On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops that will be free to all the participants. 
-This initial phases of the project will help us to provide evidence of the impact of AIR in a children of different backgrounds and evaluate their perception on the fields of AI and Robotics.
+That said, in a first phase, AIR4Children project will be piloting teaching materials with our open source robots and otto, a well known open source educational robot \cite{OttoDIY:2016}.  
+Then in a second phase, and with feedback of the pilots, teaching materials as well as the customisation of open source robots will be improved to polish a more child-centred curriculum of AIR. 
+On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops to be free of charge to all the participants. 
+In this regard, this initial phases of the project will help us to provide evidence of the impact of AIR in a children of different backgrounds and evaluate children's perception on the fields of AI and Robotics.
 
@@
 
-\subsection{Open source hardware and software}
-Adopting the philosophy of open source, AIR4Children is aiming to tackle the need of accessible and affordable resources for AI and Robotics to young audiences \cite{UNICEF2020}.
-For instance, as a way to mitigate the hight prices of educational robots, our initial prototypes of AIR4Children are in the range of EURO 100.00. 
-Such prototype, based on raspberry pi, arduino uno board and few actuators, is able to recognise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser}(a)).
-Similarly, we have identified Otto robot, a DIY educational robot, which is based on arduino, servomotors and a scratch as interface to program the robot with various routines for sensors and actuators with a price of EURO 100.00 (Fig \ref{fig:tm} (b)).
-
 \subsection{Open teaching materials}
-Considering teaching materials to be child-like oriented, AIR4Children is then adopting Montessori's education which education philosophy orbited around this quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
+Considering teaching materials of AI and Robotics to be child-like oriented, AIR4Children is then adopting Montessori's education with philosophy orbited around the quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
 In that way, materials for AIR4Children are based on Montessori education with the aim to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
@@
 numbers, size, and shapes) \cite{bers2012, resnick1998}.
-Similarly, Elkin et al.
-(2014) \cite{elkin2014}, for instance, explained how Robotics can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.
+Similarly, as Elkin et al.
+(2014) \cite{elkin2014} explained, air4children can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.
 
-That said, figure \ref{fig:tm}(a) illustrate the spiral learning technique adopted for AIR4Children to reinforce the above Montessori skills \cite{tarik2017}.
+That said, figure \ref{fig:tm}(a) illustrates the spiral learning technique adopted for AIR4Children to reinforce the above Montessori skills \cite{tarik2017}.
 

### 2021-02-14 article/tex/submission.tex
poslishes conclusions

@@
 That said, figure \ref{fig:tm}(a) illustrates the spiral learning technique adopted for AIR4Children to reinforce the above Montessori skills \cite{tarik2017}.
-
-%Finding solutions together translate to social situations as well as it provides children with the foundations for decision making, logical reasoning, categorizing, analytical thinking, negotiation, and creativity.
-%In that way, AIR4Children's workshop integrates various hands-on activities where the children will develop different intellectual and social skills to incorporate into other areas of their lives.
-%More specifically, such workshops are based on several Montessori principles such as: moving from the simple to the complex, the concrete to the abstract, the familiar to the unfamiliar and the general to the specific, as well as a mixed age group, where children can learn from each other.
 \begin{figure}[h]
@@
 \end{figure}
+
+% BLURS 
+%Finding solutions together translate to social situations as well as it provides children with the foundations for decision making, logical reasoning, categorizing, analytical thinking, negotiation, and creativity.
+%In that way, AIR4Children's workshop integrates various hands-on activities where the children will develop different intellectual and social skills to incorporate into other areas of their lives.
+%More specifically, such workshops are based on several Montessori principles such as: moving from the simple to the complex, the concrete to the abstract, the familiar to the unfamiliar and the general to the specific, as well as a mixed age group, where children can learn from each other.
 
@@
 \section{Conclusions and future work}
-We introduced the term air4project as a project with the aim to tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation of children in the fields of AI and Robotics as well as to create a more child-centre approach for AI and Robotics.
-In this work, we also touched on the open source projects in AI and Robotics as a corner stone for AIR4Children with the aim of minimise cost of the materials and made customised educational material.
-Similarly, it has been presented the three phases for AIR4Children for piloting, implementing and refining workshops for children in the age range between 6 to 14. 
-We also touched on the creation of curriculums with Montessori education, a non-traditional educational approach to help young audiences to develop skills such as think creatively with curiosity and open-minded as well as develop a have a sense of wonder and joy in learning.
+We introduced the term air4project as a project with the aim to tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation of children in the fields of AI and Robotics as well as to create teaching materials with a more child-centre approach for AI and Robotics.
+We also touched on the open source projects in AI and Robotics as a corner stone for AIR4Children with the aim of minimise cost of the materials and made customised educational materials.  
+Similarly, it has been presented the initial phases of AIR4Children that include piloting, implementing and refining workshops for children in the age range between 6 to 14 to be implemented in Xicohtzinco, a town from Tlaxcala, M\'exico.
+We also touched on the creation of curriculums with Montessori education, a non-traditional educational approach to help young audiences to develop skills to think creatively with curiosity and open-minded as well as to develop a sense of wonder and joy in learning.
 
-For future plans, in the coming year, we will complete the first round of educational material for a child-centre AI and robotics where pilots, workshops and showcases are part of the 2021 and 2022 agenda.
+As a future work, air4children aims to run workshops by the end of 2021 to put in practice educational material of child-centre AI and robotics and to evaluate the impact on these fields to children and to the community.
 

### 2021-02-20 article/tex/main.tex
:fire: initial commit for latex ci build [skip-all]

--- 2021-02-14 article/tex/submission.tex
@@
 \begin{acks}
-To Robert, for the bagels and explaining CMYK and color spaces.
+To Rocio Montenegro for her input as Montessori teacher. To Elva Corona for her contributions on giving vision to the goals of the project. 
+To Marta Perez, Donato Badillo Jr and Antonio Badillo for their interest and initial testers of the project. 
+To Angel Mandujano for his help on the preparation of the software frameworks for the project. 
+To all of you of whom has limited time and had not able you to contributed as you wished in the project.
+Thanks everyone to believe in this project, good things are ahead of us. Miguel Xochicale.
 \end{acks}

### 2021-02-20 article/tex/main.tex
refactors tex and makefile to ci and local build; adds gitignore
ammends workflow; adds reference-simple and amends main.tex
ammeds main.tex with no modifications; moves references; ammends Makefile
submitted version

@@
     \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
+
+%\usepackage[%
+%    style=ieee,
+%    dashed=false,
+%    doi=false,
+%    isbn=false,
+%    giveninits=true,
+%    maxnames=10,
+%]{biblatex}
+%\usepackage{biblatex}
+%\addbibresource{../references/references-simple.bib}
 
@@
 Similarly, we propose to follow the philosophy of Montessori education 
-to help children to not only develop matematical thinking but also to internalise new concepts and learning skills through activities of movement and repetition with open source robots.
+to help children to not only develop mathematical thinking but also to internalise new concepts and learning skills through activities of movement and repetition with open source robots.
 Finally, we add conclusions and mainly we pose the future work to go of AIR4children to putting in practice what is proposed here and measure the impact on AI and robotics of children. 
@@
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{../references/references}
+\bibliography{../references/references-simple}
+%\printbibliography
 

### 2021-02-21 article/tex/main.tex
create a new branch; and amends mathematical thinking to computational thinking

@@
 Similarly, we propose to follow the philosophy of Montessori education 
-to help children to not only develop mathematical thinking but also to internalise new concepts and learning skills through activities of movement and repetition with open source robots.
+to help children to not only develop computational thinking but also to internalise new concepts and learning skills through activities of movement and repetition with open source robots.
 Finally, we add conclusions and mainly we pose the future work to go of AIR4children to putting in practice what is proposed here and measure the impact on AI and robotics of children. 
@@
 One potential way to develop such skills is by designing activities in AI and robotics that are appropriately introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts (e.g.
-numbers, size, and shapes) \cite{bers2012, resnick1998}.
+numbers, size, and shapes) and computational thinking (e.g.
+variables, loops, counters, etc) \cite{bers2012, resnick1998}.
 Similarly, as Elkin et al.

### 2021-02-28 slides/main.tex
:fire: adds slides

\documentclass[xcolor={dvipsnames},aspectratio=169,10pt]{beamer}
\input{preamble.tex}

\title{air4children: Artificial Intelligence and Robotics for Children}
%\subtitle{...}
\author{
R. Montenegro,
E. Corona,
A. Mandujano,
D. Badillo-Perez,
D. Cruz,
{\bf Miguel Xochicale}
}
\date{
Workshop Child-Robot Interaction \& Child's Fundamental Rights at \faHashtag HRI2021\\
March 08, 2021
}
\institute{
    \faTwitter @air4children  \faGithubAlt @air4children
	\faEnvelope air4children@gmail.com
		}

\titlegraphic{
  \begin{tikzpicture}[overlay, remember picture]
    \node[%
      above right=0.35cm and -0.2cm of current page footer area.south west,
      anchor=south west,
      inner sep=0pt] {%
      \usebeamerfont{footline}
      \begin{tabular}{lm{.8\textwidth}}
        \href{http://creativecommons.org/licenses/by/4.0/}{\ccby} &
        This slices is licensed under a
	\href{http://creativecommons.org/licenses/by/4.0/}
		{Creative Commons ``Attribution 4.0 International''} license. 
	\par Get source of this slides and see further references 
		from \url{https://github.com/air4children/hri2021}.
      \end{tabular}
    };
    \node[%
      above left=0.35cm and 0cm of current page footer area.south east,
      anchor=south east,
      inner sep=0pt]{\qrcode[height=1.5cm]{https://github.com/mxochicale/}};
  \end{tikzpicture}
}

\begin{document}

\maketitle

\begin{frame}{Contents}
    \tableofcontents
\end{frame}

\input{sources/intro}
\input{sources/air4children}
\input{sources/conclusions-future-work}

\begin{frame}[standout]
  Thanks \\
  Questions?
\end{frame}

\end{document}

### 2021-02-28 slides/sources/air4children.tex
:fire: adds slides

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Teaching materials}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Subsection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Lastname N. YEAR in journal of...}
\begin{frame}{Teaching materials}
      \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{./figures/teaching-materials/versions/drawing-v01.png}
        %\caption{}
      \end{figure}
\end{frame}
}

### 2021-02-28 slides/sources/conclusions-future-work.tex
:fire: adds slides

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future work}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
\paper{Lastname N. YEAR in journal of...}
\begin{frame}{Conclusions}

  \begin{columns}
    \begin{column}{.3\linewidth}
      Towards a more realistic
  \begin{itemize}
    \item \textbf{A}
    \item \textbf{B}
    \item \textbf{C}
    \item \textbf{D}
  \end{itemize}

    \end{column}

  \begin{column}{.6\linewidth}

      \begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{./figures/future-work/versions/drawing-v00.png}
      \end{figure}

    \end{column}
  \end{columns}

\end{frame}
}

### 2021-03-02 slides/main.tex
polishes main slide

@@
 E. Corona,
+D. Badillo-P\'erez,
 A. Mandujano,
-D. Badillo-Perez,
 D. Cruz,
@@
 \date{
-Workshop Child-Robot Interaction \& Child's Fundamental Rights at \faHashtag HRI2021\\
+Workshop Child-Robot Interaction \& Child's Fundamental Rights at {\bf \#HRI2021} \\
 March 08, 2021
@@
 \institute{
-    \faTwitter @air4children  \faGithubAlt @air4children
-	\faEnvelope air4children@gmail.com
+	\faEnvelope   air4children@gmail.com \\
+	\faGithubAlt @air4children \faTwitter @air4children  
 		}
@@
       anchor=south east,
-      inner sep=0pt]{\qrcode[height=1.5cm]{https://github.com/mxochicale/}};
+      inner sep=0pt]{\qrcode[height=1.5cm]{https://github.com/air4children/hri2021}};
   \end{tikzpicture}

### 2021-03-02 slides/sources/introduction.tex
re-organise layout of the slides

--- 2021-02-28 slides/sources/air4children.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Teaching materials}
+\section{Introduction}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Subsection}
+\subsection{The progress of AI and Robotics (AIR)}
 
@@
 {
-\paper{Lastname N. YEAR in journal of...}
-\begin{frame}{Teaching materials}
+\paper{Savage N. 2021 in Nature}
+\begin{frame}{The progress of AI and Robotics in USA, China and EU}
       \begin{figure}
         \centering
-        \includegraphics[width=1.0\textwidth]{./figures/teaching-materials/versions/drawing-v01.png}
+        %\includegraphics[width=1.0\textwidth]{./figures/air4children/versions/drawing-v02.png}
         %\caption{}
@@
 }
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Open source software and hardware in AIR}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{
+\paper{Savage N. 2021 in Nature}
+\begin{frame}{Open source software and hardware in AIR}
+      \begin{figure}
+        \centering
+        %\includegraphics[width=1.0\textwidth]{./figures/air4children/versions/drawing-v02.png}
+        %\caption{}
+      \end{figure}
+\end{frame}
+}

### 2021-03-02 article/tex/main.tex
fixes spelling

@@
 However, such progress also brings other challenges such as the little to none focus on a centred AIR for children as well as the challenge of making the fields of AIR available to under-represented communities.
-With regard to child-centered AIR, there is few materials and resources with poor accessble and not appropriately affortable.  
-In terms of affortability, such technologies are unreachable to young audiences from under-represented communities as recently pointed out by United Nations Children's Fund (UNICEF) \cite{UNICEF2020}.
+With regard to child-centered AIR, there is few materials and resources with poor accessible and not appropriately affordable.  
+In terms of affordability, such technologies are unreachable to young audiences from under-represented communities as recently pointed out by United Nations Children's Fund (UNICEF) \cite{UNICEF2020}.
 Therefore, this work is proposing Artificial Intelligence and Robotics for Children (AIR4Children) as a way to make AIR available to young audiences with perhaps limited resources and to creation and design tools based on open-sourced projects to address fairness and accessibility.
@@
 Such projects were the corner stone of what is known as the Open Software Initiative, founded by Bruce Perens and Eric S.
-Raymond in 1998, stating that projects must be free redistributable, code must be available and distributable, modification must be allowed, etc \cite{brasseur2018}.
+Raymond in 1998, stating that projects must be free re distributable, code must be available and distributable, modification must be allowed, etc \cite{brasseur2018}.
 Following a similar spirit that software can be used, studied, copied, modified, and redistributed without restriction, projects of open source hardware started to emerge in mid 2000s emerged (e.g., OpenCores, RepRap (3D printing), Arduino, Adafruit and SparkFun) \cite{pearce2013}.
@@
 
-%Anoother aspects as the socialbitly of robots are well explamplied with 
+%Another aspects as the sociality of robots are well explamplied with 
 %Jibo [REF], Cosmos [REF] and more recently Shelly, a tortoise-like robot, to tacke 

### 2021-03-03 article/tex/main.tex
polishes introduction with D_Cruz contributions

@@
     \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
-
-%\usepackage[%
-%    style=ieee,
-%    dashed=false,
-%    doi=false,
-%    isbn=false,
-%    giveninits=true,
-%    maxnames=10,
-%]{biblatex}
-%\usepackage{biblatex}
-%\addbibresource{../references/references-simple.bib}
 
@@
 
-\author{air4children}
+\author{AIR4Children}
 \affiliation{%
@@
 %% of authors' names for this purpose.
-\renewcommand{\shortauthors}{air4children}
+\renewcommand{\shortauthors}{AIR4Children}
 
@@
 The scientific and technological progress in the fields of Artificial Intelligence and Robotics (AIR) has been rapidly moving forward over the past decade with special focus in countries such as United States, China and Europe where support of such fields is part of their agenda \cite{Savage2020}.
-However, such progress also brings other challenges such as the little to none focus on a centred AIR for children as well as the challenge of making the fields of AIR available to under-represented communities.
-With regard to child-centered AIR, there is few materials and resources with poor accessible and not appropriately affordable.  
-In terms of affordability, such technologies are unreachable to young audiences from under-represented communities as recently pointed out by United Nations Children's Fund (UNICEF) \cite{UNICEF2020}.
-Therefore, this work is proposing Artificial Intelligence and Robotics for Children (AIR4Children) as a way to make AIR available to young audiences with perhaps limited resources and to creation and design tools based on open-sourced projects to address fairness and accessibility.
-Additionally, AIR4Children is aiming to design curriculums with an non-traditional education approach for children of different socio economical backgrounds, developmental stages or learning abilities.
+Artificial Intelligence (AI), for instance, is changing and helping various aspects of our daily lives, from entertainment to complex medicine discovery tasks. 
+Then the democratization of current AI technologies allows people without in-depth skills in maths, statistics, and programming to create their own AI solutions.
+Examples of these new open-source platforms with a high-level programming approach are PyTorch, TensorFlow, Keras, and Scikit-learn.
+However, most of these technologies use specific syntax and grammar and work with particular programming languages which makes the learning curve a complex task for children. 
+Therefore, there is research to be done in order to design and create open-source platforms that bring children closer to AI.
+Something similar happen in the case of Robotics where software-based AI solutions can deploy solutions on real robots (such as JIBO, NAO, others), however these robots are generally inaccessible for children worldwide, particularly for those of under-represented communities.
+Such challenges of unreachable technologies in AI, and extrapolated to Robotics, to young audiences 
+also include their affordability and open accessibility \cite{UNICEF2020}.
 
-For this work, as a way to minimise cost for hardware and software, section 2 review open source project as the basis of the material for AIR4Children.
-In section 3, it is presented three stages of AIR4Children including open source materials and teaching materials based on Montessori education. 
-We then conclude this work with current status of AIR for children, open source materials for hardware, software and teaching and add few words on the future work as a way to mitigate few of the challenges cited above.
+Therefore, this work coins the term of Artificial Intelligence and Robotics for Children (AIR4Children) as a way to make AI and Robotics available to young audiences from under-represented communities as well as to create and to design tools based on open-sourced projects.
+Additionally, AIR4Children aims to create, to design and to distill curriculums based on non-traditional education (i.e.
+Montessori) for children of different socio-economical background, developmental stages and learning abilities.
+
+For this work, section 2 reviews open source projects as the basis of the material for AIR4Children.
+Section 3 introduces AIR4Children as a open source project with open teaching materials based on Montessori education. 
+We then conclude with current status of AIR for children, the creation of open source materials for hardware, software and teaching resources and mentions the future work for pilots and distillation of teaching materials.
 
@@
 Similarly, as Elkin et al.
-(2014) \cite{elkin2014} explained, air4children can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.
+(2014) \cite{elkin2014} explained, AIR4Children can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.
 
@@
 
-As a future work, air4children aims to run workshops by the end of 2021 to put in practice educational material of child-centre AI and robotics and to evaluate the impact on these fields to children and to the community.
+As a future work, AIR4Children aims to run workshops by the end of 2021 to put in practice educational material of child-centre AI and robotics and to evaluate the impact on these fields to children and to the community.
 
@@
 \begin{acks}
-To Rocio Montenegro for her input as Montessori teacher. To Elva Corona for her contributions on giving vision to the goals of the project. 
-To Marta Perez, Donato Badillo Jr and Antonio Badillo for their interest and initial testers of the project. 
+To Rocio Montenegro for her contributions and input as Montessori teacher. 
+To Elva Corona for her contributions on giving vision to the goals of the project. 
+To Marta P\'erez, Donato Badillo-Per\'ez and Antonio Badillo-Per\'e\ for their interest as initial testers of the project. 
+To Leticia Vazques for her inputs as a teacher of teenagers. 
 To Angel Mandujano for his help on the preparation of the software frameworks for the project. 
-To all of you of whom has limited time and had not able you to contributed as you wished in the project.
-Thanks everyone to believe in this project, good things are ahead of us. Miguel Xochicale.
+To Dago Cruz for his contributions on open source AI and Robotics.
+To all of you of whom with the limited time were able to contribute to this work to make it more solid.
+Thanks to Miguel Xochicale to orchestrate this project.
 \end{acks}
@@
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{../references/references-simple}
-%\printbibliography
+\bibliography{../references/references}
 

### 2021-03-03 article/tex/main.tex
polishes OA Hard-software with contributions of D_Cruz

@@
 \section{Open Source Software and Hardware for AI and Robotics}
-In 1978 Donald Knuth designed \TeX, typesetting system, which is a role model for open source projects where organisational phases of its development and the relative and simple accessibility to users were crucial to its success \cite{gaudeul2007}.
+Open source resources "refers to something people can modify and share because its design is publicly accessible" \cite{opensource2021}.
+Such open source community was initiated in 1978 by Donald Knuth who designed \TeX, typesetting system, which is a role model for open source projects where organisational phases of its development and the relative and simple accessibility to users were crucial to its success \cite{gaudeul2007}.
 Then, in 1983 Richard Stallman, with the frustration to not freely inspect, modify or share software, founded the GNU project to then create a GNU manifesto \cite{stallman1985}.
-Such projects were the corner stone of what is known as the Open Software Initiative, founded by Bruce Perens and Eric S.
+Both \TeX and GNU project were the corner stone of what is known today as the Open Software Initiative, founded by Bruce Perens and Eric S.
 Raymond in 1998, stating that projects must be free re distributable, code must be available and distributable, modification must be allowed, etc \cite{brasseur2018}.
-Following a similar spirit that software can be used, studied, copied, modified, and redistributed without restriction, projects of open source hardware started to emerge in mid 2000s emerged (e.g., OpenCores, RepRap (3D printing), Arduino, Adafruit and SparkFun) \cite{pearce2013}.
+Following a similar spirit that software can be used, studied, copied, modified, and redistributed without restriction, projects of open source hardware started to emerge in mid 2000s (e.g., OpenCores, RepRap (3D printing), Arduino, Adafruit and SparkFun) \cite{pearce2013}.
 
-Then, in the last decade, another wave of scientific innovation has been emerging in the field of AI due to open source software frameworks (e.g.
-pytorch, tensorflow, etc.) and places to distribute these (e.g.
-GitHub, gitlab, bitbucket) \cite{matelabs2017}.
-However, little has been done for child-centred AI and Robotics. 
-For instance, Otto DIY is an educational open source robot founded in 2016 by Camilo Parra, where the community of OTTO has more than 20,000 users from 20 countries and more than 100 re-designs of the robot \cite{OttoDIY:2016}.
+Then, in the last decade, another wave of scientific innovation for open source resources started with open source software frameworks (e.g.
+pytorch, tensorflow, etc.) along with places to distribute these (e.g.
+GitHub, gitlab, bitbucket, etc) \cite{matelabs2017}.
+However, our understanding is that little has been done for child-centred AI and Robotics. 
+For instance, Otto DIY is an educational open source robot founded in 2016 by Camilo Parra, where the community of Otto has more than 20,000 users from 20 countries and more than 100 re-designs of the robot \cite{OttoDIY:2016}.
 Another example is the JPL Open Source Rover, created by engineers at NASA and initially released in April 2018, which it is designed with detailed instructions for constructions for mainly high school students, and open source technical specifications, 3D models and assembly instructions \cite{OSR:2018}.
-Recently, engineers at NVIDIA in 2019, released nano JetBot as a affordable, education and fun platform  "to give the hands on experience needed to create entirely new AI projects" \cite{nanoJetBot:2019}.
+Recently, engineers at NVIDIA in 2019, released nano JetBot platform  "to give the hands on experience needed to create entirely new AI projects" \cite{nanoJetBot:2019}.
 
-That said, there is opportunity to create educational resources to teach AI and robotics to children aiming to be, as pointed by JetBot, affordable, educational and fun \cite{nanoJetBot:2019}, where our prototype, explained in next section, is starting to tackle few of them.
-Table~\ref{tab:opensourceprojects} summarises open source projects with year of establishment and cost.
+On other hand, there is an inherent engagement in children with robots as a way to use robots to enact education solutions \cite{druga2019}. 
+They take advantage of real-time deployments from computers/mobile into real robots based on the Do-It-Yourself approach. 
+Thus, the platforms encourage programming skills in children. 
+Shybo is a robot that combines open-source hardware and software \cite{Lupetti2017}.
+Shybo can perceive sounds and react through non-verbal behaviors (movements and lights). 
+The creators claim that Shybo can also be used in educational contexts to support playful learning experiences. 
+Sparky is an Arduino-based mobile robot. Creators provide schematics, 3D model files, and source code underneath are all open source \cite{sparky2012}. 
+Using block or code programming, Sparky introduces programming from elementary-age to adults.
+
+That being said, there is opportunity to create educational resources to teach AI and Robotics to children aiming to be, as pointed by the project JetBot, "affordable, educational and fun" \cite{nanoJetBot:2019} as well as to have child-centred programming languages.
 
 %BLURS
-
 %One example is the implementation of a low-cost robot with convolutional neural networks that recognise six basic face emotions: 
@@
 Similarly, we have identified Otto robot, a DIY educational robot, which is based on arduino, servomotors and a scratch as interface to program the robot with various routines for sensors and actuators with a price of EURO 100.00 (Fig \ref{fig:tm} (b)).
+In addition to the release of JPL Open Source Rover by engineers at NASA in April 2018 with a price of 2500 USD \cite{OSR:2018} or
+nano JetBot platform developed by engineers at NVIDIA in March 2019 with a price of 212 EUROS \cite{nanoJetBot:2019}. 
+See Table~\ref{tab:opensourceprojects} that summarises open source projects with year of establishment and cost.
 
@@
 
-That said, in a first phase, AIR4Children project will be piloting teaching materials with our open source robots and otto, a well known open source educational robot \cite{OttoDIY:2016}.  
+That said, in a first phase, AIR4Children project will be piloting teaching materials with our open source robots and Otto, a well known open source educational robot \cite{OttoDIY:2016}.  
 Then in a second phase, and with feedback of the pilots, teaching materials as well as the customisation of open source robots will be improved to polish a more child-centred curriculum of AIR. 

### 2021-03-03 article/tex/main.tex
polishes section air4children

@@
 
-That said, in a first phase, AIR4Children project will be piloting teaching materials with our open source robots and Otto, a well known open source educational robot \cite{OttoDIY:2016}.  
-Then in a second phase, and with feedback of the pilots, teaching materials as well as the customisation of open source robots will be improved to polish a more child-centred curriculum of AIR. 
+In a first phase, AIR4Children project will be piloting teaching materials with our open source robots and Otto, a well known open source educational robot \cite{OttoDIY:2016}.  
+Then in a second phase, and with feedback of the pilots, teaching materials with child-centre programing languages as well as the customisation of open source robots will be improved to polish a more child-centred curriculum of AIR.
 On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops to be free of charge to all the participants. 
@@
 \subsection{Open teaching materials}
-Considering teaching materials of AI and Robotics to be child-like oriented, AIR4Children is then adopting Montessori's education with philosophy orbited around the quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
-In that way, materials for AIR4Children are based on Montessori education with the aim to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
+Considering teaching materials of AI and Robotics to be child-like oriented, AIR4Children is then adopting Montessori's education with the philosophy orbited around the quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
+In that way, materials for AIR4Children are based on Montessori education to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
 %For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
@@
 Similarly, as Elkin et al.
-(2014) \cite{elkin2014} explained, AIR4Children can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.
+(2014) \cite{elkin2014} explained, AIR4Children can provide a way to engage children in problem-solving activities to allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.
 
-That said, figure \ref{fig:tm}(a) illustrates the spiral learning technique adopted for AIR4Children to reinforce the above Montessori skills \cite{tarik2017}.
+That said, figure \ref{fig:tm}(a) illustrates the spiral learning technique adopted for AIR4Children to reinforce the above Montessori skills \cite{tarik2017}, fig \ref{fig:tm}(b) shows material of otto robot to develop creative exploration and engage in collaborative activitities and fig \ref{fig:tm}(c) a block diagram as a child-centre programing language.
+
 \begin{figure}[h]

### 2021-03-03 article/tex/main.tex
polishes conclusions and future work

@@
 \section{Conclusions and future work}
-We introduced the term air4project as a project with the aim to tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation of children in the fields of AI and Robotics as well as to create teaching materials with a more child-centre approach for AI and Robotics.
+In this work, we coin the term AIR4Children as a project that aims to tackle aspects of inclusion, accessibility, transparency, equity, fairness and participation of children in the fields of AI and Robotics as well as to create teaching materials with a more child-centre approach for AI and Robotics.
 We also touched on the open source projects in AI and Robotics as a corner stone for AIR4Children with the aim of minimise cost of the materials and made customised educational materials.  
 Similarly, it has been presented the initial phases of AIR4Children that include piloting, implementing and refining workshops for children in the age range between 6 to 14 to be implemented in Xicohtzinco, a town from Tlaxcala, M\'exico.
-We also touched on the creation of curriculums with Montessori education, a non-traditional educational approach to help young audiences to develop skills to think creatively with curiosity and open-minded as well as to develop a sense of wonder and joy in learning.
+We also touched on the creation of curriculums with Montessori education, a non-traditional educational approach to help young audiences to develop skills to think creatively, with curiosity and open-minded as well as to develop a sense of wonder and joy for learning.
 
-As a future work, AIR4Children aims to run workshops by the end of 2021 to put in practice educational material of child-centre AI and robotics and to evaluate the impact on these fields to children and to the community.
+As a future work, AIR4Children aims to run workshops by the end of 2021 to put in practice educational material of child-centre AI and Robotics and to evaluate the impact on these fields to children and to the community.
 
@@
 To Dago Cruz for his contributions on open source AI and Robotics.
-To all of you of whom with the limited time were able to contribute to this work to make it more solid.
-Thanks to Miguel Xochicale to orchestrate this project.
+To all of you of whom with the limited time were able to contribute to this work to make a bit more solid.
+Thanks to Miguel Xochicale to orchestrate AIR4Children.
 \end{acks}

### 2021-03-03 article/tex/main.tex

@@
 \begin{abstract}
-In this work, we proposed AIR4Children, artificial intelligence for children, as a way to (a) tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation and (b) to create affordable child-centred materials in AI and robotics.
-We present current challenges and opportunities for a child-centred approaches for AI and robotics (AIR). 
-Similarly, we touch on open-sourced software and hardware technologies to make a more inclusive, transparent and fair participation of children in areas of AIR. 
+We introduce AIR4Children, Artificial Intelligence for Children, as a way to (a) tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation and (b) to create affordable child-centred materials in AI and Robotics (AIR).
+We present current challenges and opportunities for a child-centred approaches for AIR. 
+Similarly, we touch on open-sourced software and hardware technologies to make a more inclusive, affordable and fair participation of children in areas of AIR. 
 Then, we describe the avenues that AIR4Children can take with the development of open-sourced software and hardware.
-Similarly, we propose to follow the philosophy of Montessori education 
-to help children to not only develop computational thinking but also to internalise new concepts and learning skills through activities of movement and repetition with open source robots.
-Finally, we add conclusions and mainly we pose the future work to go of AIR4children to putting in practice what is proposed here and measure the impact on AI and robotics of children. 
+Similarly, we propose to follow the philosophy of Montessori education to help children to not only develop computational thinking but also to internalise new concepts and learning skills through activities of movement and repetition with open source robots.
+Finally, we conclude with few anecdotal experiences of our work and mainly we pose the future work of putting in practice what is proposed here to measure the impact on AIR in children of different socio-economical background, developmental stages and learning abilities.
 \end{abstract}

### 2021-03-03 article/tex/main.tex
#7 tackles reviews

@@
 Similarly, we touch on open-sourced software and hardware technologies to make a more inclusive, affordable and fair participation of children in areas of AIR. 
-Then, we describe the avenues that AIR4Children can take with the development of open-sourced software and hardware.
-Similarly, we propose to follow the philosophy of Montessori education to help children to not only develop computational thinking but also to internalise new concepts and learning skills through activities of movement and repetition with open source robots.
-Finally, we conclude with few anecdotal experiences of our work and mainly we pose the future work of putting in practice what is proposed here to measure the impact on AIR in children of different socio-economical background, developmental stages and learning abilities.
+Then, we describe the avenues that AIR4Children can take with the development of open-sourced software and hardware based on our initial pilots and experiences.
+Similarly, we propose to follow the philosophy of Montessori education to help children to not only develop computational thinking but also to internalise new concepts and learning skills through activities of movement and repetition.
+Finally, we conclude with the opportunities of our work and mainly we pose the future work of putting in practice what is proposed here to measure the potential impact on AIR in children of different socio-economical background, developmental stages and learning abilities.
 \end{abstract}
@@
 
+\subsection{Initial pilots of AIR4Children}
+In 2013, a custom-make robot of 50USD were build to teach robotics to one child in which the challenging were to teach complex concepts in a fun way without any curriculum nor teaching materials. 
+Then, in 2014, we managed to build a new robot prototype that make use of voice commands for easy interaction with children (Figure \ref{fig:teaser}(a)). 
+With such prototype, we engaged with four children of a age range between 9 to 11, who enjoyed the voice command interaction of trying to move the robot in five commands (move forward, move backward, move right, move left and stop) (top image of Figure \ref{fig:teaser}(c)).
+Recently, during three months from October 2020, we managed to virtually pilot Otto robot to one child accompanied with his mother for the constructions and the teaching of basis of AIR (bottom image of Figure \ref{fig:teaser}(c)).
+Such pilots help us to clarify and to distill the aims of AIR4Children as a way to go for another round of pilots which will include curriculums and teaching materials to help both children, instructors (and perhaps their parents as well).
+
 %% BLURS 
@@
 We also touched on the open source projects in AI and Robotics as a corner stone for AIR4Children with the aim of minimise cost of the materials and made customised educational materials.  
-Similarly, it has been presented the initial phases of AIR4Children that include piloting, implementing and refining workshops for children in the age range between 6 to 14 to be implemented in Xicohtzinco, a town from Tlaxcala, M\'exico.
-We also touched on the creation of curriculums with Montessori education, a non-traditional educational approach to help young audiences to develop skills to think creatively, with curiosity and open-minded as well as to develop a sense of wonder and joy for learning.
+We added our previous experience of few pilots since 2013 as way to narrow down the aims of AIR4Children.
+Similarly, it has been presented the initial phases of AIR4Children that include piloting, implementing and refining workshops for children in the age range between 6 to 14 (to be implemented in Xicohtzinco, a town from Tlaxcala, M\'exico).
+We also touched on the creation of curriculums following the philosophy of Montessori education, a non-traditional educational approach to help young audiences to develop skills to think creatively, with curiosity and open-minded and to develop a sense of wonder and joy for learning.
 
-As a future work, AIR4Children aims to run workshops by the end of 2021 to put in practice educational material of child-centre AI and Robotics and to evaluate the impact on these fields to children and to the community.
+As a future work, AIR4Children aims to run workshops by the end of 2021 to put in practice educational material of child-centre AI and Robotics and to evaluate the impact on these fields to children, parents and their community.
 

### 2021-03-03 article/tex/main.tex
#7 correct spell errors

@@
 In a first phase, AIR4Children project will be piloting teaching materials with our open source robots and Otto, a well known open source educational robot \cite{OttoDIY:2016}.  
-Then in a second phase, and with feedback of the pilots, teaching materials with child-centre programing languages as well as the customisation of open source robots will be improved to polish a more child-centred curriculum of AIR.
+Then in a second phase, and with feedback of the pilots, teaching materials with child-centre programming languages as well as the customisation of open source robots will be improved to polish a more child-centred curriculum of AIR.
 On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops to be free of charge to all the participants. 
@@
 
-That said, figure \ref{fig:tm}(a) illustrates the spiral learning technique adopted for AIR4Children to reinforce the above Montessori skills \cite{tarik2017}, fig \ref{fig:tm}(b) shows material of otto robot to develop creative exploration and engage in collaborative activitities and fig \ref{fig:tm}(c) a block diagram as a child-centre programing language.
+That said, figure \ref{fig:tm}(a) illustrates the spiral learning technique adopted for AIR4Children to reinforce the above Montessori skills \cite{tarik2017}, fig \ref{fig:tm}(b) shows material of otto robot to develop creative exploration and engage in collaborative activities and fig \ref{fig:tm}(c) a block diagram as a child-centre programming language.
 
@@
 To Marta P\'erez, Donato Badillo-Per\'ez and Antonio Badillo-Per\'e\ for their interest as initial testers of the project. 
-To Leticia Vazques for her inputs as a teacher of teenagers. 
+To Leticia V\'azquez for her inputs as a teacher of teenagers. 
 To Angel Mandujano for his help on the preparation of the software frameworks for the project. 

### 2021-03-03 article/tex/main.tex
#7 aligns coclusions and abstract

@@
 Similarly, we propose to follow the philosophy of Montessori education to help children to not only develop computational thinking but also to internalise new concepts and learning skills through activities of movement and repetition.
-Finally, we conclude with the opportunities of our work and mainly we pose the future work of putting in practice what is proposed here to measure the potential impact on AIR in children of different socio-economical background, developmental stages and learning abilities.
+Finally, we conclude with the opportunities of our work and mainly we pose the future work of putting in practice what is proposed here to evaluate the potential impact on AIR to children, instructors, parents and their community.
 \end{abstract}
@@
 
-As a future work, AIR4Children aims to run workshops by the end of 2021 to put in practice educational material of child-centre AI and Robotics and to evaluate the impact on these fields to children, parents and their community.
+As a future work, AIR4Children aims to run workshops by the end of 2021 to put in practice educational material of child-centre AI and Robotics and to evaluate the impact on these fields to children, instructors, parents and their community.
 

### 2021-03-06 slides/sources/introduction.tex
#5 adds notes for images to be added
adds chars for progress of air and its references [skip-all]

@@
 {
-\paper{Savage N. 2021 in Nature}
+%\paper{Savage N. 2021 in Nature, DOI: doi.org/10.1038/d41586-020-03409-8}
+\paper{Zhang D. et al 2021 in AI 2021 Index Report, Fig 4.3.3 https://aiindex.stanford.edu/report/}
+
 \begin{frame}{The progress of AI and Robotics in USA, China and EU}
+
 \begin{figure}
  \centering
-        %\includegraphics[width=1.0\textwidth]{./figures/air4children/versions/drawing-v02.png}
+ \includegraphics[width=1.0\textwidth]{./figures/progress-of-air/versions/drawing-v00.png}
  %\caption{}
 \end{figure}
+
+\end{frame}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{
+%\paper{Savage N. 2021 in Nature, DOI: doi.org/10.1038/d41586-020-03409-8}
+\paper{Zhang D. et al 2021 in AI 2021 Index Report, Fig 1.1.19 https://aiindex.stanford.edu/report/}
+
+\begin{frame}{The progress of AI and Robotics in USA, China and EU}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=1.0\textwidth]{./figures/progress-of-air/versions/drawing-v02.png}
+ %\caption{}
+\end{figure}
+
+\end{frame}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{
+%\paper{Savage N. 2021 in Nature, DOI: doi.org/10.1038/d41586-020-03409-8}
+\paper{Zhang D. et al 2021 in AI 2021 Index Report, Fig 1.1.19 https://aiindex.stanford.edu/report/}
+
+\begin{frame}{The progress of AI and Robotics in USA, China and EU}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=1.0\textwidth]{./figures/progress-of-air/versions/drawing-v01.png}
+ %\caption{}
+\end{figure}
+
 \end{frame}
@@
 \begin{frame}{Open source software and hardware in AIR}
+
+* add time line of OS SH in AIR
       \begin{figure}

### 2021-03-06 slides/sources/air4children.tex
re-organise layout of the slides
#5 adds notes for images to be added
incorporates montesory and team figures
polish structure a bit the strucutre
adds robots and use same name for AIR4Children in the slides

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Teaching materials}
+\section{AIR4Children}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Subsection}
+\subsection{AIR for Children}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{
+\paper{Savage N. 2021 in Nature}
+\begin{frame}{Title}
+      \begin{figure}
+        \centering
+        \includegraphics[width=1.0\textwidth]{./figures/air4children/versions/drawing-v00.png}
+        %\caption{}
+      \end{figure}
+\end{frame}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{
+\paper{Savage N. 2021 in Nature}
+\begin{frame}{Title}
+      \begin{figure}
+        \centering
+        \includegraphics[width=1.0\textwidth]{./figures/air4children/versions/drawing-v01.png}
+        %\caption{}
+      \end{figure}
+\end{frame}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Teaching Materials}
 
@@
 \paper{Lastname N. YEAR in journal of...}
-\begin{frame}{Teaching materials}
+\begin{frame}{Montessori}
+
+    \begin{figure}
+        \centering
+        \includegraphics[width=1.0\textwidth]{./figures/montessori/versions/drawing-v00.png}
+        %\caption{}
+      \end{figure}
+\end{frame}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{
+\paper{Lastname N. YEAR in journal of...}
+\begin{frame}{Teaching materials based on Montessori}
+* add image that represents montesory skills
       \begin{figure}

### 2021-03-07 slides/sources/air4children.tex
polishes prototypes of air4children [skip-all]
polishes teaching section [skip-all]

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{AIR for Children}
+\subsection{Prototyping and Piloting Open Source Robots}
 
@@
 {
-\paper{Savage N. 2021 in Nature}
-\begin{frame}{Title}
+\paper{Xochicale M. 2014 \it{Libre Robotics (proposal)} }
+\begin{frame}{Prototyping Open Source Robots}
       \begin{figure}
@@
 {
-\paper{Savage N. 2021 in Nature}
-\begin{frame}{Title}
+\paper{Xochicale M. 2015 in Mecate; Parra C. et al. 2016, \it{Otto DIY}}
+\begin{frame}{Piloting robot prototypes}
       \begin{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Teaching Materials}
+\subsection{Teaching Materials based on Montessori Education and Spiral Learning}
 
@@
 {
-\paper{Lastname N. YEAR in journal of...}
-\begin{frame}{Montessori}
+\paper{Elkin M., Sullivan A, Bers 2014 in Journal of Informantion and Technology}
+\begin{frame}{AI and Robotics curriculum in Montessori Classroom}
 
+  \it{The hand is the instrument of the mind.} Dr. Maria Montessori (1970-1952).
     \begin{figure}
@@
 {
-\paper{Lastname N. YEAR in journal of...}
-\begin{frame}{Teaching materials based on Montessori}
-* add image that represents montesory skills
+\paper{Mohammad T. et al., 2017; Harden R. M. and Stamper N in Journal of Medical Teacher}
+\begin{frame}{Adopting Spiral Learning Methods in AIR4Children}
+
   \begin{figure}
         \centering
-        \includegraphics[width=1.0\textwidth]{./figures/teaching-materials/versions/drawing-v01.png}
+        \includegraphics[width=1.0\textwidth]{./figures/teaching-materials/versions/drawing-v02.png}
         %\caption{}

### 2021-03-07 slides/sources/air4children.tex
polished spiral learning fig [skip-all]

@@
 \paper{Elkin M., Sullivan A, Bers 2014 in Journal of Informantion and Technology}
-\begin{frame}{AI and Robotics curriculum in Montessori Classroom}
-
-  \it{The hand is the instrument of the mind.} Dr. Maria Montessori (1970-1952).
+\begin{frame}{Adopting Montessori Education in AIR4Children curriculum} 
+  \vspace{3mm}
+  \it{"The hand is the instrument of the mind."} Dr. Maria Montessori (1970-1952).
+  \vspace{2mm}
     \begin{figure}
@@
 {
-\paper{Mohammad T. et al., 2017; Harden R. M. and Stamper N in Journal of Medical Teacher}
-\begin{frame}{Adopting Spiral Learning Methods in AIR4Children}
+\paper{Mohammad T. et al., 2017; Harden R. M. 1999 in Journal of Medical Teacher}
+\begin{frame}{Adopting Spiral Learning Methods in AIR4Children curriculum}
 

### 2021-03-07 slides/sources/conclusions-future-work.tex
re-organise layout of the slides
#5 adds notes for images to be added
incorporates montesory and team figures
polishes conclusions and future work [skip-all]

@@
 {
-\paper{Lastname N. YEAR in journal of...}
-\begin{frame}{Conclusions}
+%\paper{Lastname N. YEAR in journal of...}
+\begin{frame}{Conclusions and future work}
 
   \begin{columns}
-    \begin{column}{.3\linewidth}
-      Towards a more realistic
+  \begin{column}{.75\linewidth}
+
+  \textbf{Conclusions}
+
+  We proposed AIR4children to create
   \begin{itemize}
-    \item \textbf{A}
-    \item \textbf{B}
-    \item \textbf{C}
-    \item \textbf{D}
+    \item a more inclusive, affortable and fair participation of children in AI and Robotics
+    \item child-centred AI and Robotics based on Spiral Learning and Montessori Education 
+    \item Open source robots to be affortable and fun 
+  \end{itemize}
+
+  \textbf{Future work}
+  \begin{itemize}
+    \item Piloting air4children in Xicohtzinco, M\'exico
+    \item Evaluation of the impact of AIR to children, instructors and parents. %(and perhaps their community).
   \end{itemize}
@@
 
-  \begin{column}{.6\linewidth}
+  \begin{column}{.3\linewidth}
 
@@
 }
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{
+\paper{Lastname N. YEAR in journal of...}
+\begin{frame}{Acknowledgements}
+
+      \begin{figure}
+        \centering
+        \includegraphics[width=0.9\textwidth]{./figures/team/versions/drawing-v00.png}
+      \end{figure}
+
+\end{frame}
+}

### 2021-03-07 slides/sources/conclusions-future-work.tex
adds photos of brain and adriana to the acknowledgements section
polished and potentially the last version of the slides

@@
   \begin{itemize}
-    \item a more inclusive, affortable and fair participation of children in AI and Robotics
-    \item child-centred AI and Robotics based on Spiral Learning and Montessori Education 
+    \item a more inclusive, affortable and fair participation of children in AI and Robotics,
+    \item child-centred AI and Robotics based on Spiral Learning and Montessori Education, and
     \item Open source robots to be affortable and fun 
@@
   \begin{itemize}
-    \item Piloting air4children in Xicohtzinco, M\'exico
+    \item Piloting AIR4Children in Xicohtzinco, M\'exico
     \item Evaluation of the impact of AIR to children, instructors and parents. %(and perhaps their community).
@@
 {
-\paper{Lastname N. YEAR in journal of...}
+%\paper{Lastname N. YEAR in journal of...}
 \begin{frame}{Acknowledgements}
@@
   \centering
-        \includegraphics[width=0.9\textwidth]{./figures/team/versions/drawing-v00.png}
+  \includegraphics[width=1.0\textwidth]{./figures/team/versions/drawing-v00.png}
   \end{figure}

### 2021-03-08 slides/gif-slides/pdf2gif.sh
polishes main README and polish pdf2gif and adds gif [skip-all]

@@ -1,12 +1,7 @@
 #!/bin/bash
 
-# pdf2gif.sh
-# chmod +x pdf2gif.sh
-
 # References
 # http://phyletica.org/imagemagick/
-
-
 
 # cp pdf to /slides-gif
 echo '(1) cp pdf to /slides-gif'
@@ -14,13 +9,15 @@ cp ../*.pdf .
 
 # pdf2png
 echo '(2) pdf2png'
-convert -density 600 *.pdf -strip -resize @1048576 PNG8:slide-%02d.png
+convert -density 500 *.pdf -strip -resize @1048576 PNG8:slide-%02d.png
 
 # png2gif
 echo '(3) png2gif'
-convert -layers OptimizePlus -delay 75 slide-0?.png slide-??.png -loop 0 slides.gif
+convert -layers OptimizePlus -delay 75 slide-??.png -loop 0 slides.gif
+## delay 50 in each slides and then loop it! 
+
 #convert -layers OptimizePlus -delay 75 slide-0?.png slide-1[01234].png -delay 300 slide-1[567].png -loop 0 slides.gif
-# The options in the command above specify to spend 3/4 of a second on the first 15 slides, and then 3 seconds on the last three slides. 
+## The options in the command above specify to spend 3/4 of a second on the first 15 slides, and then 3 seconds on the last three slides. 
 
 # delete png images
 echo '(4) remove *.png *.pdf'

### 2021-03-08 slides/main.tex
polishes maketitle
re-organise layout of the slides
add Leticia in the coauthors

@@
 
-\title{air4children: Artificial Intelligence and Robotics for Children}
+\title{AIR4Children: Artificial Intelligence and Robotics for Children}
 %\subtitle{...}
@@
 A. Mandujano,
+L. V\'azquez,
 D. Cruz,
@@
 \date{
-Workshop Child-Robot Interaction \& Child's Fundamental Rights at {\bf \#HRI2021} \\
+Workshop on Child-Robot Interaction \& Child's Fundamental Rights at {\bf \#HRI2021} \\
 March 08, 2021
@@
 
-\input{sources/intro}
+\input{sources/introduction}
 \input{sources/air4children}
@@
 
-\begin{frame}[standout]
-  Thanks \\
-  Questions?
-\end{frame}
+%\begin{frame}[standout]
+%  Thanks \\
+%  Questions?
+%\end{frame}
+
+\maketitle
 

### 2021-03-08 slides/sources/air4children.tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Teaching Materials based on Montessori Education and Spiral Learning}
+\subsection{Adopting Montessori Education and Spiral Learning}
 
@@
 \paper{Elkin M., Sullivan A, Bers 2014 in Journal of Informantion and Technology}
-\begin{frame}{Adopting Montessori Education in AIR4Children curriculum} 
+\begin{frame}{Adopting Montessori Education in the curriculum of AIR4Children } 
   \vspace{3mm}
@@
 \paper{Mohammad T. et al., 2017; Harden R. M. 1999 in Journal of Medical Teacher}
-\begin{frame}{Adopting Spiral Learning Methods in AIR4Children curriculum}
+\begin{frame}{Adopting Spiral Learning Methods in the curriculum of AIR4Children}
 

### 2021-03-13 article/arxiv/A_copy-tex-figures.sh
adds arxiv v01 improving its submission process along with its submission

@@ -1,0 +1,8 @@
+## copy tex file
+mkdir -p files
+cp ../tex/main.tex files
+## cp image files to arxiv path
+cp ../../article/figures/air4children/versions/drawing-v01.png files
+#mv files/drawing-v01.png files/air4children.png
+cp ../../article/figures/teaching-materials/versions/drawing-v00.png files
+#mv files/drawing-v00.png files/teaching-materials.png 

### 2023-03-11 slides/sources/air4children.tex

@@
         \centering
-        \includegraphics[width=1.0\textwidth]{./figures/air4children/versions/drawing-v00.png}
+        \includegraphics[width=1.0\textwidth]{./figures/air4children-a/outputs/drawing-v00.png}
         %\caption{}
@@
         \centering
-        \includegraphics[width=1.0\textwidth]{./figures/air4children/versions/drawing-v01.png}
+        \includegraphics[width=1.0\textwidth]{./figures/air4children-b/outputs/drawing-v00.png}
         %\caption{}
@@
         \centering
-        \includegraphics[width=1.0\textwidth]{./figures/montessori/versions/drawing-v00.png}
+        \includegraphics[width=1.0\textwidth]{./figures/montessori/outputs/drawing-v00.png}
         %\caption{}
@@
         \centering
-        \includegraphics[width=1.0\textwidth]{./figures/teaching-materials/versions/drawing-v02.png}
+        \includegraphics[width=1.0\textwidth]{./figures/teaching-materials/outputs/drawing-v02.png}
         %\caption{}

### 2023-03-11 slides/sources/conclusions-future-work.tex

@@
         \centering
-        \includegraphics[width=0.9\textwidth]{./figures/future-work/versions/drawing-v00.png}
+        \includegraphics[width=0.9\textwidth]{./figures/logo/outputs/drawing-v00.png}
       \end{figure}
@@
   \centering
-  \includegraphics[width=1.0\textwidth]{./figures/team/versions/drawing-v00.png}
+  \includegraphics[width=1.0\textwidth]{./figures/team/outputs/drawing-v00.png}
   \end{figure}

### 2023-03-11 slides/sources/introduction.tex
adds timeline-osh [skip-all]

--- 2021-03-02 slides/sources/introduction.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The progress of AI and Robotics (AIR)}
+\subsection{Education, Investment and Publications in AI and Robotics (AIR)}
 
@@
 {
-\paper{Savage N. 2021 in Nature}
+%\paper{Savage N. 2021 in Nature, DOI: doi.org/10.1038/d41586-020-03409-8}
+\paper{Zhang D. et al 2021 in AI 2021 Index Report, Fig 4.3.3 https://aiindex.stanford.edu/report/}
+
 \begin{frame}{The progress of AI and Robotics in USA, China and EU}
+
 \begin{figure}
  \centering
-        %\includegraphics[width=1.0\textwidth]{./figures/air4children/versions/drawing-v02.png}
+ \includegraphics[width=1.0\textwidth]{./figures/progress-of-air-a/outputs/drawing-v00.png}
  %\caption{}
 \end{figure}
+
+\end{frame}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{
+%\paper{Savage N. 2021 in Nature, DOI: doi.org/10.1038/d41586-020-03409-8}
+\paper{Zhang D. et al 2021 in AI 2021 Index Report, Fig 1.1.19 https://aiindex.stanford.edu/report/}
+
+\begin{frame}{The progress of AI and Robotics in USA, China and EU}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=1.0\textwidth]{./figures/progress-of-air-b/outputs/drawing-v00.png}
+ %\caption{}
+\end{figure}
+
+\end{frame}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+{
+%\paper{Savage N. 2021 in Nature, DOI: doi.org/10.1038/d41586-020-03409-8}
+\paper{Zhang D. et al 2021 in AI 2021 Index Report, Fig 1.1.19 https://aiindex.stanford.edu/report/}
+
+\begin{frame}{The progress of AI and Robotics in USA, China and EU}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=1.0\textwidth]{./figures/progress-of-air-c/outputs/drawing-v00.png}
+ %\caption{}
+\end{figure}
+
 \end{frame}
@@
 {
-\paper{Savage N. 2021 in Nature}
+%\paper{Savage N. 2021 in Nature}
 \begin{frame}{Open source software and hardware in AIR}
+
       \begin{figure}
         \centering
-        %\includegraphics[width=1.0\textwidth]{./figures/air4children/versions/drawing-v02.png}
+        \includegraphics[width=1.0\textwidth]{./figures/timeline-osh/outputs/drawing-v00.png}
         %\caption{}
